---
title: "COVID-19 Eric's Dashboard"
#author: "Eric Cabrera Estupinan"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: fill
    social: ["twitter", "facebook", "menu"]
    source_code: embed
runtime: shiny
---

```{r setup, include=FALSE}
rm(list=ls()) #clean up the memory
library(ggplot2)
library(tidyverse)
library(flexdashboard)
library(knitr)
library(htmlwidgets)
library(DT)
library(tibble)
library(dplyr)
library(highcharter)
library(RColorBrewer)
library(viridis)
library(tidyr)
library(xts)
library(lubridate)
library(sf)
library(leaflet)
library(prophet)
library(shiny)
library(dygraphs)
library(broom)
library(deSolve)
library(fs)
```

```{r}
row_data2<-read.csv("data/single_nations.csv", header = T)
row_data2$iso_code<-as.character(row_data2$iso_code)
row_data2$country<-as.character(row_data2$country)
##-----------------------------------------------------------------------------------

#Load local Maps data
#------------------------
load("data/Countries.RData")
#------------------------

##Load from local "row_data1" and "row_data2" just for testing
row_data1<-read_csv("data/row_data1.csv", col_types = cols())
row_data1<-row_data1[ ,2:9]
#------------------------------

#daily_data_update
#-----------------------------------------------------------------------------------
curr_date<-(row_data1[max(which(row_data1$iso_code==c("ABW"))), 2])    
curr_date<-as.character(curr_date$date)      #Year-month-day

min_date<-(row_data1[1, 2])
min_date<-as.character(min_date$date)
max_date<-curr_date
#-----------------------------------------------------------------------------------

## merge bouth tables --------------------------------------
data1<-left_join(row_data1,row_data2,by="iso_code")
#-----------------------------------------------------------
## Remove unused variables----------------------------------
rm(total_cases, total_deaths, total_recovered, row_data1, count_codes)
#-----------------------------------------------------------

data1<- data1[ , c("iso_code", "country", "date", "total_cases", "total_deaths", "total_recovered", "new_cases", "new_deaths", "new_recovered", "year", "gdp_percap", "life_expect", "population","region","income")]

data1<- data1 %>% 
  group_by(country) %>% 
  mutate(CFR=round((total_deaths/total_cases)*100, digits = 2), 
         CRR=round((total_recovered/total_cases)*100, digits = 2),
         factor1=round((total_cases*100000)/population, digits = 2),
         factor2=round((total_deaths*100000)/population, digits = 2),
         factor3=round((total_recovered*100000)/population, digits=2)) %>% 
  ungroup()

data1$new_deaths<- if_else(data1$new_deaths<0, 0, data1$new_deaths) 
data1$new_recovered<- if_else(data1$new_recovered<0, 0, data1$new_recovered) 
data1$new_cases<- if_else(data1$new_cases<0, 0, data1$new_cases) 
```

World data
======================================

Column {.sidebar}
------------------------------------------------------------------

```{r select-input27}

dateInput(inputId = 'si_world', 
          label = 'Select date', 
          value = max_date,
          min = min_date, 
          max = max_date,
          format="yyyy-mm-dd")
```

Row
---------------------------------------------------------------------------------------

### **Updated**

```{r}

valueBox(paste(curr_date),
         color="warning")
```

### **Total confirmed cases** 

```{r}
renderValueBox({

date_w<-input$si_world
valueBox(data1 %>%
           filter(date==date_w) %>%
           summarise(sum(total_cases)),
         icon = "fa-users")
})
```

### **New confirmed cases**

```{r}
renderValueBox({

date_w<-input$si_world  
valueBox(data1 %>%
           filter(date==date_w) %>%
           summarise(sum(new_cases)),
         icon = "fa-ambulance")
})  
```

### **Total confirmed deaths**

```{r}
renderValueBox({

date_w<-input$si_world  
valueBox(data1 %>%
           filter(date==date_w) %>%
           summarise(sum(total_deaths)),
         icon = "fa-hospital",
         color="red")
})
```

### **New confirmed deaths**

```{r}
renderValueBox({
  
date_w<-input$si_world 
valueBox(data1 %>%
           filter(date==date_w) %>%
           summarise(sum(new_deaths)),
         icon = "fa-hospital",
         color="red")
})  
```

### **Total confirmed recovered**

```{r}
renderValueBox({

date_w<-input$si_world   
valueBox(data1 %>%
           filter(date==date_w) %>%
           summarise(sum(total_recovered)),
         icon = "fa-heartbeat",
         color="green")
})
```

### **New confirmed recovered**

```{r}
renderValueBox({
  
date_w<-input$si_world  
valueBox(data1 %>%
           filter(date==date_w) %>%
           summarise(sum(new_recovered)),
         icon = "fa-heartbeat",
         color="green")
})
```

Row
---------------------------------------------------------------------------------------

### **World Case Fatality Rate CFR (%)**

```{r}
renderGauge({

date_w<-input$si_world  
f1<-data1 %>%
           filter(date==date_w) %>%
           summarise(sum(total_cases))

f2<-data1 %>%
           filter(date==date_w) %>%
           summarise(sum(total_deaths))

let<-as.numeric((f2/f1)*100)
gauge(round(let,
            digits = 2),
            min=0,
            max=10,
            gaugeSectors(success = c(0, 3),
                         warning=c(3, 7),
                         danger=c(7, 10),
                         colors=c('green', 'yellow', 'red')))
})
```


### **World Case Recovered Rate CRR (%)**

```{r}
renderGauge({  
  
date_w<-input$si_world   
f1<-data1 %>%
           filter(date==date_w) %>%
           summarise(sum(total_cases))
f3<-data1 %>%
           filter(date==date_w) %>%
           summarise(sum(total_recovered))

recov<-as.numeric((f3/f1)*100)
gauge(round(recov,
            digits = 2),
            min=0,
            max=100,
            gaugeSectors(success = c(60, 100),
                         warning=c(30, 60),
                         danger=c(0, 30),
                         colors=c('green', 'yellow', 'red')))
})
```


Row {.tabset .tabset-fade}
---------------------------------------------------------------------------------------

### **Cumulative variables TS**

```{r}

 all_data_variable<- data1 %>% 
   select(date, total_cases, total_deaths, total_recovered)
 
all_data_variable<- all_data_variable %>% 
  group_by(date) %>% 
  summarise(total_cases=sum(total_cases),
            total_deaths=sum(total_deaths),
            total_recovered=sum(total_recovered)) 
 
#cols <- brewer.pal(7, "Set1")
#cols <- c("blue","green","red")
cols <- c(brewer.pal(7, "Set1"),"black")

highchart (type="stock") %>%
  hc_add_series(data=all_data_variable,
                name="Deaths",
                type="area", 
                hcaes(x=date, y=total_deaths)) %>%    
  hc_add_series(data=all_data_variable, 
                name="Cases",
                type="area", 
                hcaes(x=date, y=total_cases)) %>% 
  hc_add_series(data=all_data_variable,
                name="Recovered",
                type="area", 
                hcaes(x=date, y=total_recovered)) %>%
hc_title(text="Cumulative total confirmed: CASES, DEATHS and RECOVERED in the world, (Time Serie, TS)",
         align="left",
         useHTML=TRUE) %>%
hc_subtitle(text="<i>Data source: https://github.com/CSSEGISandData/COVID-19/tree/master/csse_covid_19_data/csse_covid_19_time_series", 
            align="left",
            useHTML=TRUE) %>%   
hc_legend(enabled = TRUE) %>% 
  hc_exporting(enabled = TRUE,
               filename="World_cummulative_Variables", 
               formAttribute=list(target="_black"), 
               buttons=list(contextButton=list(text="Export", 
                                               theme=list(fill="transparent")))) %>%  # enable export
hc_colors(cols) %>%
hc_plotOptions(series = list(stacking = "normal",
                                marker = list(enabled = FALSE, symbol = "circle", size=1,
                                              states = list(hover = list(enabled = TRUE))),
                                lineWidth = 1,
                                lineColor="black")) %>%
hc_xAxis(title = list(text="time (days)"),
           type="datetime") %>%
hc_yAxis(title = list(text="Confirmed cases, deaths and recovered"),
         type="number",
         labels=list(format= "{value:,.0f}"),
         opposite=FALSE) %>%
hc_tooltip(shared = FALSE,
           crosshairs=TRUE,
           borderWidth = 2,
           bacgroundColor="transparent") %>% 
hc_credits(enabled = TRUE, text = "Dr. Eric Cabrera Estupinan",
            href = "http://www.htmlwidgets.org/") %>% 
hc_rangeSelector(selected = 4) %>%
hc_navigator( #outlineColor = "gray",
              outlineWidth = 2,
              series = list(color = "red",
                            lineWidth = 2,
                            type = "areaspline", # you can change the type
                            fillColor = "rgba(255, 0, 0, 0.2)"))#,
```

### **New variables TS**

```{r}

data_new_var<- data1 %>% 
  group_by(date) %>% 
  summarise(sum_new_cas=sum(new_cases, na.rm=TRUE), 
            sum_new_deaths=sum(new_deaths, na.rm=TRUE), 
            sum_new_recov=sum(new_recovered, na.rm=TRUE))

# set color palette
cols <- brewer.pal(7, "Set1")
#cols <- c("blue","green","red")

highchart (type="stock") %>%
  
  hc_add_series(data=data_new_var,
                name="New deaths",
                type="area", 
                fillColor = "rgba(255, 0, 0, 0.2)",
                hcaes(x=date, y=sum_new_deaths)) %>%    
  hc_add_series(data=data_new_var, 
                name="New cases",
                type="area",
                fillColor = "rgba(0,105,208,0.38)",
                hcaes(x=date, y=sum_new_cas)) %>% 
  hc_add_series(data=data_new_var,
                name="New recovered",
                type="area",
                fillColor = "rgba(0,207,0,0.22)",
                hcaes(x=date, y=sum_new_recov)) %>%
hc_title(text="Confirmed new: CASES, DEATHS and RECOVERED in the world, (Time Serie, TS)",
         align="left",
         useHTML=TRUE) %>%
hc_subtitle(text="<i>Data source: https://github.com/CSSEGISandData/COVID-19/tree/master/csse_covid_19_data/csse_covid_19_time_series", 
            align="left",
            useHTML=TRUE) %>%   
hc_legend(enabled = TRUE) %>%
  hc_exporting(enabled = TRUE,
               filename="World_daily_Variables", 
               formAttribute=list(target="_black"), 
               buttons=list(contextButton=list(text="Export", 
                                               theme=list(fill="transparent")))) %>%  # enable export
hc_colors(cols) %>%
hc_plotOptions(series = list(stacking = NULL,
                               marker = list(enabled = TRUE, symbol = "circle", size=1,
                                             states = list(hover = list(enabled = TRUE))),
                               lineWidth = 2,
                               fillColor="red")) %>%
hc_xAxis(title = list(text="time (days)"),
           type="datetime") %>%
hc_yAxis(title = list(text="New Cases, Deaths and Recovered"),
           labels=list(format= "{value:,.0f}"),
           opposite=FALSE) %>%
hc_tooltip(shared = FALSE,
             crosshairs=TRUE,
             bacgroundColor="transparent") %>% 
hc_credits(enabled = TRUE, text = "Dr. Eric Cabrera Estupinan",
            href = "http://www.htmlwidgets.org/") %>% 
hc_rangeSelector(selected = 4) %>%
hc_navigator( #outlineColor = "gray",
              outlineWidth = 2,
              series = list(color = "red",
                            lineWidth = 2,
                            type = "areaspline", # you can change the type
                            fillColor = "rgba(255, 0, 0, 0.2)"))#,
```

### **Cumulative variables per million TS**

```{r}

Tot_world_pop<- row_data2 %>% 
  summarise(Tot_world_peop=sum(population))

 all_data_variable<- data1 %>% 
   select(date, total_cases, total_deaths, total_recovered)

 num_rows=nrow(all_data_variable)
 
 all_data_variable<-gather(all_data_variable, "Variables", "n", 2:4)
 
 all_data_variable<- all_data_variable %>% 
   group_by(Variables, date) %>% 
   summarise(cant_val=sum(n))


all_data_variable<-all_data_variable[, c("date", "Variables", "cant_val")]
world_cum_data<-spread(all_data_variable, "Variables", "cant_val")

world_cum_data<- world_cum_data %>% 
  mutate(cases_per_million= round((total_cases*1000000)/Tot_world_pop$Tot_world_peop, digits = 2),
         deaths_per_million= round((total_deaths*1000000)/Tot_world_pop$Tot_world_peop, digits = 2),
         recovered_per_million= round((total_recovered*1000000)/Tot_world_pop$Tot_world_peop, digits = 2),
         CFR= round((total_deaths/total_cases)*100, digits = 2),
         CRR= round((total_recovered/total_cases)*100, digits = 2)) 

# set color palette
cols <- brewer.pal(7, "Set1")
#cols <- c("blue","green","red")

highchart (type="stock") %>%
  hc_add_series(data=world_cum_data,
                name="Deaths per million",
                type="line", 
                hcaes(x=date, y=deaths_per_million)) %>%   
  hc_add_series(data=world_cum_data, 
                name="Cases per million",
                type="line", 
                hcaes(x=date, y=cases_per_million)) %>% 
  hc_add_series(data=world_cum_data,
                name="Recovered per million",
                type="line", 
                hcaes(x=date, y=recovered_per_million)) %>%
hc_title(text="Confirmed: CASES, DEATHS and RECOVERED per million of people in the world, (Time Serie, TS)",
         align="left",
         useHTML=TRUE) %>%
hc_subtitle(text="<i>Data source: https://github.com/CSSEGISandData/COVID-19/tree/master/csse_covid_19_data/csse_covid_19_time_series", 
            align="left",
            useHTML=TRUE) %>%   
hc_legend(enabled = TRUE) %>% 
  hc_exporting(enabled = TRUE,
               filename="World_cumulative_variables_per_millions", 
               formAttribute=list(target="_black"), 
               buttons=list(contextButton=list(text="Export", 
                                               theme=list(fill="transparent")))) %>%  # enable export
hc_colors(cols) %>%
hc_plotOptions(series = list(stacking = NULL,
                               marker = list(enabled = TRUE, symbol = "circle", size=1,
                                             states = list(hover = list(enabled = TRUE))),
                               lineWidth = 2,
                               fillColor="red")) %>%
hc_xAxis(title = list(text="time (days)"),
           type="datetime") %>%
hc_yAxis(title = list(text="Cases, Deaths and Recovered per million"),
           labels=list(format= "{value:,.0f}"),
           opposite=FALSE) %>%
hc_tooltip(shared = FALSE,
             crosshairs=TRUE,
             bacgroundColor="transparent") %>% 
hc_credits(enabled = TRUE, text = "Dr. Eric Cabrera Estupinan",
            href = "http://www.htmlwidgets.org/") %>% 
hc_rangeSelector(selected = 4) %>%
hc_navigator( #outlineColor = "gray",
              outlineWidth = 2,
              series = list(color = "red",
                            lineWidth = 2,
                            type = "areaspline", # you can change the type
                            fillColor = "rgba(255, 0, 0, 0.2)"))
```

### **CFR and CRR TS**

```{r}

# set color palette
cols <- brewer.pal(7, "Set1")
#cols <- c("blue","green","red")

highchart (type="stock") %>%
   hc_add_series(data=world_cum_data, 
                name="CFR",
                type="line", 
                hcaes(x=date, y=CFR)) %>% 
  hc_add_series(data=world_cum_data,
                name="CRR",
                type="line", 
                hcaes(x=date, y=CRR)) %>%
hc_title(text="Case Fatality Rate CFR and Case Recovered Rate CRR in the world, (Time Serie, TS)",
         align="left",
         useHTML=TRUE) %>%
hc_subtitle(text="<i>Data source: https://github.com/CSSEGISandData/COVID-19/tree/master/csse_covid_19_data/csse_covid_19_time_series", 
            align="left",
            useHTML=TRUE) %>%   
hc_legend(enabled = TRUE) %>% 
  hc_exporting(enabled = TRUE,
               filename="World_CFR_and_CRR", 
               formAttribute=list(target="_black"), 
               buttons=list(contextButton=list(text="Export", 
                                               theme=list(fill="transparent")))) %>%  # enable export
hc_colors(cols) %>%
hc_plotOptions(series = list(stacking = NULL,
                               marker = list(enabled = TRUE, symbol = "circle", size=1,
                                             states = list(hover = list(enabled = TRUE))),
                               lineWidth = 2,
                               fillColor="red")) %>%
hc_xAxis(title = list(text="time (days)"),
           type="datetime") %>%
hc_yAxis(title = list(text="CFR and CRR"),
           labels=list(format= "{value:,.0f}%"),
           opposite=FALSE) %>%
hc_tooltip(shared = FALSE,
             crosshairs=TRUE,
             bacgroundColor="transparent") %>% 
hc_credits(enabled = TRUE, text = "Dr. Eric Cabrera Estupinan",
            href = "http://www.htmlwidgets.org/") %>% 
hc_rangeSelector(selected = 4) %>%
hc_navigator( #outlineColor = "gray",
              outlineWidth = 2,
              series = list(color = "red",
                            lineWidth = 2,
                            type = "areaspline", # you can change the type
                            fillColor = "rgba(255, 0, 0, 0.2)"))
```

Summary {data-icon="fa-list" data-orientation=columns data-navmenu="Regions"}
======================================================================================

Column {.sidebar}
------------------------------------------------------------------
```{r}

dateInput(inputId = 'si_reg', 
          label = ' Select date', 
          value = max_date,
          min = min_date, 
          max = max_date,
          format="yyyy-mm-dd")
```

```{r select-input18}

 selectInput(inputId = 'si_count11', label = 'Select cummulative variable',
             choices = c("Total Confirmed Cases", "Total Confirmed Deaths", "Total Confirmed Recovered"), 
             selected = "Total Confirmed Cases", multiple = FALSE)
```

```{r select-input19}

 selectInput(inputId = 'si_count12', label = 'Select daily variable',
             choices = c("Daily Confirmed Cases", "Daily Confirmed Deaths", "Daily Confirmed Recovered"), 
             selected = "Daily Confirmed Cases", multiple = FALSE)
```

Column {.tabset}
--------------------------------------------------------------------------------------

### Variables per: **Regions**

```{r}

totcases_reg1<- data1 %>%
  group_by(region, date) %>%
  summarize(totcases_cum=sum(total_cases, na.rm=TRUE)) %>% 
  ungroup()

renderHighchart({

date_reg<-input$si_reg
#date_reg<- curr_date

Total_reg<- data1 %>% 
  filter(date==date_reg) %>% 
  group_by(region) %>% 
  summarise(totcases_cum_reg=sum(total_cases, na.rm=TRUE),
            totdeaths_cum_reg=sum(total_deaths, na.rm=TRUE),
            totrecovered_cum_reg=sum(total_recovered, na.rm=TRUE))

cols<- brewer.pal(7, "Set1")

highchart() %>% 
hc_chart(type = "column", inverted=TRUE, polar = TRUE) %>%
hc_plotOptions(column = list(stacking = "normal", borderWidth=0, 
                             pointPadding=0, groupPadding=0.15)) %>%
hc_add_series(data=Total_reg$totdeaths_cum_reg,
              name="Total deaths") %>%   
hc_add_series(data=Total_reg$totcases_cum_reg,
              name="Total cases") %>% 
hc_add_series(data=Total_reg$totrecovered_cum_reg,
              name="Total recovered") %>% 
hc_xAxis(categories = Total_reg$region, lineWith=0) %>%
hc_yAxis(type="number",
         labels=list(format= "{value:,.0f}")) %>%  
hc_pane(size= '80%', innerSize='15%', startAngle=0, endAngle=270) %>% 

hc_title(text= paste("Main variables behavior, Regions comparison. Date:", date_reg), 
          align="left",
          useHTML=TRUE) %>% 
hc_subtitle(text="<i>Data source: https://github.com/CSSEGISandData/COVID-19/tree/master/csse_covid_19_data/csse_covid_19_time_series", 
          align="left",
          useHTML=TRUE) %>%
hc_legend(enabled = TRUE) %>% 
    hc_exporting(enabled = TRUE,
               filename="Regions_comparison_variables", 
               formAttribute=list(target="_black"), 
               buttons=list(contextButton=list(text="Export", 
                                               theme=list(fill="transparent")))) %>%  # enable export
hc_colors(cols) %>% 
hc_tooltip(outside=TRUE, borderWidth = 2, bacgroundColor="transparent") %>% 
hc_credits(enabled = TRUE, text = "Dr. Eric Cabrera Estupinan",
           href = "http://www.htmlwidgets.org/")
})

```

Column {.tabset}
--------------------------------------------------------------------------------------

### **Main variables pie**

```{r, fig.keep='none'}

renderHighchart({

Variab_obj<-input$si_count11 
#Variab_obj<-"Total Confirmed Cases"

Variab_date<-input$si_reg
#Variab_date<-curr_date

if (Variab_obj=="Total Confirmed Cases"){
  Obj_col<-data1$total_cases
  col_ptos_name="Cases"
}
if (Variab_obj=="Total Confirmed Deaths"){
  Obj_col<-data1$total_deaths
  col_ptos_name="Deaths"
}
if (Variab_obj=="Total Confirmed Recovered"){
  Obj_col<-data1$total_recovered
  col_ptos_name="Recovered"
}

data1_pie<-cbind(data1,Obj_col)

data1_pie<-data1_pie %>%
  filter(date==Variab_date) %>%
  group_by(region) %>%
  summarise(Sum_variab=sum(Obj_col))

data1_pie<- mutate(data1_pie, percent=(Sum_variab/sum(Sum_variab))*100, 
                   col_ptos="Cases", porciento="Percent")

cols <- brewer.pal(7,"Set1")

hchart(data1_pie, "pie", hcaes(x=region, y=Sum_variab), showInLegend = TRUE) %>% 
hc_colors(cols) %>%
hc_title(text= paste(Variab_obj, "per Regions of the World. Date:", Variab_date), 
          align="left",
          useHTML=TRUE) %>% 
hc_subtitle(text="<i>Data source: https://github.com/CSSEGISandData/COVID-19/tree/master/csse_covid_19_data/csse_covid_19_time_series", 
          align="left",
          useHTML=TRUE) %>%
hc_legend(enabled = TRUE) %>%
    hc_exporting(enabled = TRUE,
               filename="Main_variables_Pie", 
               formAttribute=list(target="_black"), 
               buttons=list(contextButton=list(text="Export", 
                                               theme=list(fill="transparent")))) %>%  # enable export
hc_tooltip(borderWidth = 2,
           bacgroundColor="transparent",
           pointFormat = "{point.col_ptos}: {point.Sum_variab:.0f}<br> {point.porciento}: {point.percent:.2f}%") %>% 
hc_credits(enabled = TRUE, text = "Dr. Eric Cabrera Estupinan",
           href = "http://www.htmlwidgets.org/")
})  

```

### **Main variables acummulate TS**

```{r, fig.keep='none'}

renderHighchart({

Variab_obj<-input$si_count11 
#Variab_obj<-"Total Confirmed Cases"

if (Variab_obj=="Total Confirmed Cases"){
  Obj_col<-data1$total_cases
  col_ptos_name="Cases"
}
if (Variab_obj=="Total Confirmed Deaths"){
  Obj_col<-data1$total_deaths
  col_ptos_name="Deaths"
}
if (Variab_obj=="Total Confirmed Recovered"){
  Obj_col<-data1$total_recovered
  col_ptos_name="Recovered"
}

data1_ts<-cbind(data1,Obj_col)

 tot_var_reg<- data1_ts %>%
   group_by(region, date) %>%
   summarize(totvar_cum=sum(Obj_col, na.rm=TRUE))
 
 totvar_days<- data1_ts %>%
   group_by(date) %>%
   summarize(totvarday_cum=sum(Obj_col, na.rm=TRUE))
 
 totvar_days<-mutate(totvar_days, world="World cases")
 totvar_day1<-tot_var_reg[1:nrow(totvar_days), ]
 totvar_day1$region<-totvar_days$world
 totvar_day1$date<-totvar_days$date
 totvar_day1$totvar_cum<-totvar_days$totvarday_cum

cols <- c(brewer.pal(7, "Set1"),"black")

highchart (type="stock") %>%
  
  hc_add_series(data=totvar_day1,
                name="World",
                type="line",
                color= "black",
                hcaes(x=date, y=totvar_cum)) %>% 
  hc_add_series(data<-filter(tot_var_reg,region=='East Asia & Pacific'),
                name="East Asia & Pacific",
                type="area",
                hcaes(x=date, y=totvar_cum)) %>%   
  hc_add_series(data<-filter(tot_var_reg,region=='Europe & Central Asia'),
                name="Europe & Central Asia",
                type="area",
                hcaes(x=date, y=totvar_cum)) %>%
  hc_add_series(data<-filter(tot_var_reg,region=='Latin America & Caribbean'),
                name="Latin America & Caribbean",
                type="area",
                hcaes(x=date, y=totvar_cum)) %>%  
  hc_add_series(data<-filter(tot_var_reg,region=='Middle East & North Africa'),
                name="Middle East & North Africa",
                type="area",
                hcaes(x=date, y=totvar_cum)) %>%   
  hc_add_series(data<-filter(tot_var_reg,region=='North America'),
                name="North America",
                type="area",
                hcaes(x=date, y=totvar_cum)) %>%   
  hc_add_series(data<-filter(tot_var_reg,region=='South Asia'),
                name="South Asia",
                type="area",
                hcaes(x=date, y=totvar_cum)) %>%   
  hc_add_series(data<-filter(tot_var_reg,region=='Sub-Saharan Africa'),
                name="Sub-Saharan Africa",
                type="area",
                hcaes(x=date, y=totvar_cum)) %>%   
hc_title(text=paste(Variab_obj, "by regions of the planet, (Time Serie, TS)"),
         align="left",
         useHTML=TRUE) %>%
hc_subtitle(text="<i>Data source: https://github.com/CSSEGISandData/COVID-19/tree/master/csse_covid_19_data/csse_covid_19_time_series", 
            align="left",
            useHTML=TRUE) %>%   
hc_legend(enabled = TRUE) %>% 
hc_colors(cols) %>%
hc_plotOptions(series = list(stacking = "normal",
                                marker = list(enabled = FALSE, symbol = "circle", size=1,
                                              states = list(hover = list(enabled = TRUE))),
                                lineWidth = 1,
                                lineColor="black")) %>%
hc_xAxis(title = list(text="time (days)"),
           type="datetime") %>%
hc_yAxis(title = list(text=paste(Variab_obj)),
         type="number",
         labels=list(format= "{value:,.0f}"),
         opposite=FALSE) %>%
hc_tooltip(shared = FALSE,
           crosshairs=TRUE,
           borderWidth = 2,
           bacgroundColor="transparent") %>% 
hc_credits(enabled = TRUE, text = "Dr. Eric Cabrera Estupinan",
            href = "http://www.htmlwidgets.org/") %>% 
hc_exporting(enabled = TRUE,
             filename="Regions_variables_Acummulate",
             formAttribute=list(target="_black"),
             buttons=list(contextButton=list(text="Export",
                                             theme=list(fill="transparent")))) %>%  # enable export
hc_rangeSelector(selected = 4) %>%
hc_navigator( #outlineColor = "gray",
              outlineWidth = 2,
              series = list(color = "red",
                            lineWidth = 2,
                            type = "areaspline", # you can change the type
                            fillColor = "rgba(255, 0, 0, 0.2)"))#,  
})

```

### **Main variables daily TS**

```{r, fig.keep='none'}

renderHighchart({

Variab_obj<-input$si_count12 
#Variab_obj<-"Daily Confirmed Cases"

if (Variab_obj=="Daily Confirmed Cases"){
  Obj_col1<-data1$new_cases
  col_ptos_name="Cases"
}
if (Variab_obj=="Daily Confirmed Deaths"){
  Obj_col1<-data1$new_deaths
  col_ptos_name="Deaths"
}
if (Variab_obj=="Daily Confirmed Recovered"){
  Obj_col1<-data1$new_recovered
  col_ptos_name="Recovered"
}

data1_ts1<-cbind(data1,Obj_col1)

var_reg<- data1_ts1 %>%
  group_by(region, date) %>%
  summarize(var_day=sum(Obj_col1, na.rm=TRUE))

varnew_days<- data1_ts1 %>%
  group_by(date) %>%
  summarize(varnewday_cum=sum(Obj_col1, na.rm=TRUE))

varnew_days<-mutate(varnew_days, region="World cases")

data_spr1<-spread(var_reg, region, var_day)
data_spr2<-spread(varnew_days, region, varnewday_cum)

Countr_sel<-as.character(c("East Asia & Pacific","Europe & Central Asia",
                           "Latin America & Caribbean","Middle East & North Africa",
                           "North America","South Asia", "Sub-Saharan Africa"))

data_xts1<- xts(data_spr1[ ,Countr_sel], order.by=data_spr1$date)    
data_xts2<- xts(data_spr2[ ,"World cases"], order.by=data_spr2$date)

cols <- brewer.pal(7,"Set1")

hc1<- highchart(type="stock") %>%
  hc_colors(cols) %>%
  hc_add_series(data=data_xts2$`World cases` , name = "World cases", color="black") %>%
  hc_add_series(data=data_xts1$`East Asia & Pacific` , name="East Asia & Pacific") %>%
  hc_add_series(data=data_xts1$`Europe & Central Asia`, name = "Europe & Central Asia") %>%
  hc_add_series(data=data_xts1$`Latin America & Caribbean`, name = "Latin America & Caribbean") %>%
  hc_add_series(data=data_xts1$`Middle East & North Africa`, name = "Middle East & North Africa") %>%
  hc_add_series(data=data_xts1$`North America`, name = "North America") %>%
  hc_add_series(data=data_xts1$`South Asia`, name = "South Asia") %>%
  hc_add_series(data=data_xts1$`Sub-Saharan Africa`, name = "Sub-Saharan Africa") %>%
hc_title(text=paste(Variab_obj,"by regions of the planet, (Time Serie, TS)"),
         align="left",
         useHTML=TRUE) %>%
hc_subtitle(text="<i>Data source: https://github.com/CSSEGISandData/COVID-19/tree/master/csse_covid_19_data/csse_covid_19_time_series", 
            align="left",
            useHTML=TRUE) %>%   
hc_legend(enabled = TRUE) %>% 
  hc_exporting(enabled = TRUE,
             filename="Regions_variables_Daily",
             formAttribute=list(target="_black"),
             buttons=list(contextButton=list(text="Export",
                                             theme=list(fill="transparent")))) %>%  # enable export
hc_plotOptions(series = list(stacking = NULL, fillOpacity=0.1,
                             marker = list(enabled = FALSE, 
                                           symbol = "circle",
                                           states = list(hover = list(enabled = TRUE))),
                             lineWidth = 2,
                             fillColor="red")) %>%
hc_xAxis(title = list(text="time (days)"),
           type="datetime") %>%
hc_yAxis(title = list(text=paste(Variab_obj)),
           labels=list(format= "{value:,.0f}"),
           opposite=FALSE) %>%
hc_tooltip(shared = FALSE,
             borderColor = "black",
             crosshairs=TRUE,
             bacgroundColor="transparent") %>% 
hc_credits(enabled = TRUE, text = "Dr. Eric Cabrera Estupinan",
            href = "http://www.htmlwidgets.org/")
hc1 %>% 
hc_rangeSelector(selected = 4) %>%
hc_navigator( #outlineColor = "gray",
              outlineWidth = 2,
              series = list(color = "red",
                            lineWidth = 2,
                            type = "areaspline", # you can change the type
                            fillColor = "rgba(255, 0, 0, 0.2)"))
})

```

Pick a region {data-icon="fa-line-chart" data-orientation=rows data-navmenu="Regions"}
==========================================================================================

Column {.sidebar}
------------------------------------------------------------------

```{r select-input20}

Region_list_main<-data1 %>% 
  select(region) %>% 
  distinct(region)

Region_list_main<-as.character(Region_list_main$region)

 selectInput(inputId = 'si_region_main', 
             label = ' Select a Region',
             choices = Region_list_main, 
             selected = "Latin America & Caribbean")
```

```{r select-input28}

dateInput(inputId = 'si_reg_1', 
          label = 'Select date', 
          value = max_date,
          min = min_date, 
          max = max_date,
          format="yyyy-mm-dd")
```

Row
---------------------------------------------------------------------------------------

### **Updated**

```{r}
valueBox(paste(curr_date),
         color="warning")
```

### **Total confirmed cases** 

```{r}
renderValueBox({

region_main_sel<-input$si_region_main
date_reg1<-input$si_reg_1
valueBox(data1 %>% filter(date==date_reg1) %>% 
           filter(region==region_main_sel) %>% 
           summarise(sum(total_cases)),
         icon = "fa-users")
})
```

### **New confirmed cases**

```{r}
renderValueBox({

region_main_sel<-input$si_region_main  
date_reg1<-input$si_reg_1
valueBox(data1 %>% filter(date==date_reg1) %>%
           filter(region==region_main_sel) %>% 
           summarise(sum(new_cases)),
         icon = "fa-ambulance")
})
```

### **Total confirmed deaths**

```{r}
renderValueBox({

region_main_sel<-input$si_region_main 
date_reg1<-input$si_reg_1
valueBox(data1 %>% filter(date==date_reg1) %>%
           filter(region==region_main_sel) %>%
           summarise(sum(total_deaths)),
         icon = "fa-hospital",
         color="red")
})  
```

### **New confirmed deaths**

```{r}
renderValueBox({

region_main_sel<-input$si_region_main
date_reg1<-input$si_reg_1
valueBox(data1 %>% filter(date==date_reg1) %>%
           filter(region==region_main_sel) %>%
           summarise(sum(new_deaths)),
         icon = "fa-hospital",
         color="red")
})  
```

### **Total confirmed recovered**

```{r}
renderValueBox({
 
region_main_sel<-input$si_region_main 
date_reg1<-input$si_reg_1
valueBox(data1 %>% filter(date==date_reg1) %>%
           filter(region==region_main_sel) %>%
           summarise(sum(total_recovered)),
         icon = "fa-heartbeat",
         color="green")
})  
```

### **New confirmed recovered**

```{r}
renderValueBox({
  
region_main_sel<-input$si_region_main 
date_reg1<-input$si_reg_1
valueBox(data1 %>% filter(date==date_reg1) %>%
           filter(region==region_main_sel) %>%
           summarise(sum(new_recovered)),
         icon = "fa-heartbeat",
         color="green")
})
```

Row
---------------------------------------------------------------------------------------

### **Region Case Fatality Rate CFR (%)**

```{r}
renderGauge({

region_main_sel<-input$si_region_main
date_reg1<-input$si_reg_1
ff1<-data1 %>%
  filter(date==date_reg1) %>% 
  filter(region==region_main_sel) %>%
  summarise(sum(total_cases))

ff2<-data1 %>%
  filter(date==date_reg1) %>% 
  filter(region==region_main_sel) %>%
  summarise(sum(total_deaths))

let_mainregion<-as.numeric((ff2/ff1)*100)
gauge(round(let_mainregion,
            digits = 2),
            min=0,
            max=10,
            gaugeSectors(success = c(0, 3),
                         warning=c(3, 7),
                         danger=c(7, 10),
                         colors=c('green', 'yellow', 'red')))
})
```

### **Region Case Recovered Rate CRR (%)**

```{r}
renderGauge({

region_main_sel<-input$si_region_main 
date_reg1<-input$si_reg_1
ff1<-data1 %>%
  filter(date==date_reg1) %>% 
  filter(region==region_main_sel) %>%
  summarise(sum(total_cases))

ff3<-data1 %>% 
  filter(date==date_reg1) %>% 
  filter(region==region_main_sel) %>%
  summarise(sum(total_recovered))

recov_mainregion<-as.numeric((ff3/ff1)*100)
gauge(round(recov_mainregion,
            digits = 2),
            min=0,
            max=100,
            gaugeSectors(success = c(60, 100),
                         warning=c(30, 60),
                         danger=c(0, 30),
                         colors=c('green', 'yellow', 'red')))
})
```


Row {.tabset .tabset-fade}
---------------------------------------------------------------------------------------

### **Region map**
```{r}

World_count3=World_count

 for (i in 1:nrow(row_data2)){
    
   count_name=as.character(row_data2[i, 2])
    if (count_name != "Bonaire, Sint Eustatius and Saba"
     & count_name != "Channel Islands"
     & count_name != "Guadeloupe"
     & count_name != "French Guiana"
     & count_name != "Martinique"
     & count_name != "Mayotte"
     & count_name != "West Bank and Gaza"
     & count_name != "Reunion"){
      
   World_count3[which(World_count3$country==count_name), 3]=row_data2[i,9]
   World_count3[which(World_count3$country==count_name), 4]=row_data2[i,10]
   World_count3[which(World_count3$country==count_name), 5]=row_data2[i,11]
 } else {}
 }     

renderLeaflet({
 
region_main_sel<-input$si_region_main 
#region_main_sel<-c("Latin America & Caribbean")  
  
nf<-which(World_count3$REGION_WB==region_main_sel)
reg_plot<-World_count3[nf, ]

leaflet(options = leafletOptions(dragging=TRUE,
                                 minZoom = 2.2,
                                 maxZoom = 18,
                                 preferCanvas = TRUE)) %>% 
  addTiles(group = "OMS (default)") %>%
  addProviderTiles("CartoDB", group="CartoDB", 
                   options = providerTileOptions(updateWhenZooming=FALSE,
                                                 updateWhenIdle = TRUE)) %>% 
  addPolygons(data = reg_plot,
               fillColor = "blue", 
               color = "blue",
               fillOpacity = .1,
               label = ~country) %>% 
  setView(lng = 0, lat=40, zoom= 2.2) %>% 
  addGraticule(interval = 20, style = list(color = "gray", weight = 1), group="Graticule") %>% 
  addLayersControl(baseGroups = c("OSM (default)", "CartoDB"),    
    overlayGroups=c("Graticule"),
    options = layersControlOptions(collapsed = TRUE)) %>% 
  addMiniMap(tiles = providers$Esri.WorldStreetMap,
    toggleDisplay = TRUE) %>% 
    addScaleBar(position = "bottomright", options = scaleBarOptions(maxWidth = 100, 
                                                                    metric = TRUE,
                                                                    updateWhenIdle = TRUE)) %>%
    addMeasure(position="bottomleft",
               primaryLengthUnit = "meters",
               primaryAreaUnit = "sqmeters",
               activeColor = "#3D535D",
               completedColor = "#7D4479",
               localization=de)
})
```

### **Cumulative variables TS**

```{r}

 renderHighchart({
 
 region_main_sel<-input$si_region_main 
#region_main_sel<-c("Latin America & Caribbean")
 
 Main_region_data_var<-data1 %>% 
   filter(region==region_main_sel) %>%
   group_by(date) %>% 
   summarise(total_cases=sum(total_cases), total_deaths=sum(total_deaths), total_recovered=sum(total_recovered))
#   select(date, country, region, total_cases, total_deaths, total_recovered)
 
 cols <- c(brewer.pal(7, "Set1"),"black")
 
 highchart (type="stock") %>%
   
 hc_add_series(data=Main_region_data_var,
                 name="Deaths",
                 type="area",
                 hcaes(x=date, y=total_deaths)) %>% 
 hc_add_series(data=Main_region_data_var,
                 name="Cases",
                 type="area",
                 hcaes(x=date, y=total_cases)) %>%    
 hc_add_series(data=Main_region_data_var,
                 name="Recovered",
                 type="area",
                 hcaes(x=date, y=total_recovered)) %>% 
 hc_title(text=paste("Cumulative total confirmed CASES, DEATHS & RECOVERED in:", region_main_sel,"(Time Serie, TS)"),
         align="left",
         useHTML=TRUE) %>%
hc_subtitle(text="<i>Data source: https://github.com/CSSEGISandData/COVID-19/tree/master/csse_covid_19_data/csse_covid_19_time_series",
            align="left",
            useHTML=TRUE) %>%
hc_legend(enabled = TRUE) %>%
hc_exporting(enabled = TRUE) %>%  # enable export
hc_colors(cols) %>%
hc_plotOptions(series = list(stacking = "normal",
                                marker = list(enabled = FALSE, symbol = "circle", size=1,
                                              states = list(hover = list(enabled = TRUE))),
                                lineWidth = 1,
                                lineColor="black")) %>%
hc_xAxis(title = list(text="time (days)"),
           type="datetime") %>%
hc_yAxis(title = list(text="Confirmed cases, deaths & recovered"),
         type="number",
         labels=list(format= "{value:,.0f}"),
         opposite=FALSE) %>%
hc_tooltip(shared = FALSE,
           crosshairs=TRUE,
           borderWidth = 2,
           bacgroundColor="transparent") %>%
hc_credits(enabled = TRUE, text = "Dr. Eric Cabrera Estupinan",
            href = "http://www.htmlwidgets.org/") %>%
hc_rangeSelector(selected = 4) %>%
hc_navigator( #outlineColor = "gray",
              outlineWidth = 2,
              series = list(color = "red",
                            lineWidth = 2,
                            type = "areaspline", # you can change the type
                            fillColor = "rgba(255, 0, 0, 0.2)"))
 })
```

### **New variables TS**

```{r}

renderHighchart({
  
 region_main_sel<-input$si_region_main 
#region_main_sel<-c("Latin America & Caribbean")

Main_region_data_newvar<-data1 %>% 
  filter(region==region_main_sel) %>%
  group_by(date) %>% 
  summarise(new_cases=sum(new_cases), new_deaths=sum(new_deaths), new_recovered=sum(new_recovered))
  
# set color palette
cols <- brewer.pal(7, "Set1")
#cols <- c("blue","green","red")

highchart (type="stock") %>%

  hc_add_series(data=Main_region_data_newvar,
                name="New deaths",
                type="area",
                fillColor = "rgba(255, 0, 0, 0.2)",
                hcaes(x=date, y=new_deaths)) %>%    
  hc_add_series(data=Main_region_data_newvar, 
                name="New cases",
                type="area",
                fillColor = "rgba(0,105,208,0.38)",
                hcaes(x=date, y=new_cases)) %>% 
  hc_add_series(data=Main_region_data_newvar,
                name="New recovered",
                type="area",
                fillColor = "rgba(0,207,0,0.22)",
                hcaes(x=date, y=new_recovered)) %>%
hc_title(text=paste("Confirmed new: CASES, DEATHS and RECOVERED in", region_main_sel, "(Time Serie, TS)"),
         align="left",
         useHTML=TRUE) %>%
hc_subtitle(text="<i>Data source: https://github.com/CSSEGISandData/COVID-19/tree/master/csse_covid_19_data/csse_covid_19_time_series", 
            align="left",
            useHTML=TRUE) %>%   
hc_legend(enabled = TRUE) %>% 
hc_exporting(enabled = TRUE) %>%  # enable export
hc_colors(cols) %>%
hc_plotOptions(series = list(stacking = NULL,
                               marker = list(enabled = TRUE, symbol = "circle", size=1,
                                             states = list(hover = list(enabled = TRUE))),
                               lineWidth = 2,
                               fillColor="red")) %>%
hc_xAxis(title = list(text="time (days)"),
           type="datetime") %>%
hc_yAxis(title = list(text="New Cases, Deaths and Recovered"),
           labels=list(format= "{value:,.0f}"),
           opposite=FALSE) %>%
hc_tooltip(shared = FALSE,
             crosshairs=TRUE,
             bacgroundColor="transparent") %>% 
hc_credits(enabled = TRUE, text = "Dr. Eric Cabrera Estupinan",
            href = "http://www.htmlwidgets.org/") %>% 
hc_rangeSelector(selected = 4) %>%
hc_navigator( #outlineColor = "gray",
              outlineWidth = 2,
              series = list(color = "red",
                            lineWidth = 2,
                            type = "areaspline", # you can change the type
                            fillColor = "rgba(255, 0, 0, 0.2)"))#,   

})
```

### **Cumulative variables per 100000 inhabitant TS**

```{r}

renderHighchart({

 region_main_sel<-input$si_region_main 
#region_main_sel<-c("Latin America & Caribbean")

 
Main_region_data_inhab<-data1 %>% 
  filter(region==region_main_sel) %>%
  group_by(date) %>% 
  summarise(total_cases=sum(total_cases), 
            total_deaths=sum(total_deaths), 
            total_recovered=sum(total_recovered),
            population=sum(population)) 

Main_region_data_inhab<- Main_region_data_inhab %>% 
  mutate(factor1=round(((total_cases/population)*100000), digits = 2),
         factor2=round(((total_deaths/population)*100000), digits = 2),
         factor3=round(((total_recovered/population)*100000), digits = 2))

# set color palette
cols <- brewer.pal(7, "Set1")
#cols <- c("blue","green","red")

highchart (type="stock") %>%

  hc_add_series(data=Main_region_data_inhab,
                name="Deaths per 100000 inhab",
                type="line", 
                hcaes(x=date, y=round(factor2, digits = 2))) %>%    
  hc_add_series(data=Main_region_data_inhab, 
                name="Cases per 100000 inhab",
                type="line", 
                hcaes(x=date, y=round(factor1, digits = 2))) %>%   
  hc_add_series(data=Main_region_data_inhab,
                name="Recovered per 100000 inhab",
                type="line", 
                hcaes(x=date, y=round(factor3, digits = 2))) %>%
hc_title(text=paste("Cumulative total confirmed: CASES, DEATHS and RECOVERED per 100000 inhab in", region_main_sel, "(Time Serie, TS)"),
         align="left",
         useHTML=TRUE) %>%
hc_subtitle(text="<i>Data source: https://github.com/CSSEGISandData/COVID-19/tree/master/csse_covid_19_data/csse_covid_19_time_series", 
            align="left",
            useHTML=TRUE) %>%   
hc_legend(enabled = TRUE) %>% 
hc_exporting(enabled = TRUE) %>%  # enable export
hc_colors(cols) %>%
hc_plotOptions(series = list(stacking = NULL,
                               marker = list(enabled = TRUE, symbol = "circle", size=1,
                                             states = list(hover = list(enabled = TRUE))),
                               lineWidth = 2,
                               fillColor="red")) %>%
hc_xAxis(title = list(text="time (days)"),
           type="datetime") %>%
hc_yAxis(title = list(text="Cases, Deaths and Recovered per 100000 inhab"),
           labels=list(format= "{value:,.0f}"),
           opposite=FALSE) %>%
hc_tooltip(shared = FALSE,
             crosshairs=TRUE,
             bacgroundColor="transparent") %>% 
hc_credits(enabled = TRUE, text = "Dr. Eric Cabrera Estupinan",
            href = "http://www.htmlwidgets.org/") %>% 
hc_rangeSelector(selected = 4) %>%
hc_navigator( #outlineColor = "gray",
              outlineWidth = 2,
              series = list(color = "red",
                            lineWidth = 2,
                            type = "areaspline", # you can change the type
                            fillColor = "rgba(255, 0, 0, 0.2)"))#,   
})
```
 
### **CFR and CRR TS**

```{r}

renderHighchart({
  
region_main_sel<-input$si_region_main 
#region_main_sel<-c("Latin America & Caribbean")

Main_count_data_cfr_crr<-data1 %>% 
  filter(region==region_main_sel) %>%
  group_by(date) %>% 
  summarise(total_cases=sum(total_cases), 
            total_deaths=sum(total_deaths), 
            total_recovered=sum(total_recovered))

Main_count_data_cfr_crr<- Main_count_data_cfr_crr %>% 
  mutate(CFR=round(((total_deaths/total_cases)*100), digits = 2),
         CRR=round(((total_recovered/total_cases)*100), digits = 2))
  
# set color palette
cols <- brewer.pal(7, "Set1")
#cols <- c("blue","green","red")

highchart (type="stock") %>%
  
  hc_add_series(data=Main_count_data_cfr_crr, 
                name="CFR",
                type="line", 
                hcaes(x=date, y=round(CFR, digits = 2))) %>% 
  hc_add_series(data=Main_count_data_cfr_crr,
                name="CRR",
                type="line", 
                hcaes(x=date, y=round(CRR, digits = 2))) %>%
hc_title(text=paste("Case Fatality Rate CFR and Case Recovered Rate CRR in", region_main_sel,"(Time Serie, TS)"),
         align="left",
         useHTML=TRUE) %>%
hc_subtitle(text="<i>Data source: https://github.com/CSSEGISandData/COVID-19/tree/master/csse_covid_19_data/csse_covid_19_time_series", 
            align="left",
            useHTML=TRUE) %>%   
hc_legend(enabled = TRUE) %>% 
hc_exporting(enabled = TRUE) %>%  # enable export
hc_colors(cols) %>%
hc_plotOptions(series = list(stacking = NULL,
                               marker = list(enabled = TRUE, symbol = "circle", size=1,
                                             states = list(hover = list(enabled = TRUE))),
                               lineWidth = 2,
                               fillColor="red")) %>%
hc_xAxis(title = list(text="time (days)"),
           type="datetime") %>%
hc_yAxis(title = list(text="CFR and CRR"),
           labels=list(format= "{value:,.0f}%"),
           opposite=FALSE) %>%
hc_tooltip(shared = FALSE,
             crosshairs=TRUE,
             bacgroundColor="transparent") %>% 
hc_credits(enabled = TRUE, text = "Dr. Eric Cabrera Estupinan",
            href = "http://www.htmlwidgets.org/") %>% 
hc_rangeSelector(selected = 4) %>%
hc_navigator( #outlineColor = "gray",
              outlineWidth = 2,
              series = list(color = "red",
                            lineWidth = 2,
                            type = "areaspline", # you can change the type
                            fillColor = "rgba(255, 0, 0, 0.2)"))#,   

})
```


All regions map {data-icon="fa-map-o" data-orientation=columns data-navmenu="Regions"}
==========================================================================================

Column {.sidebar}
------------------------------------------------------------------
```{r select-input}

dateInput(inputId = 'si_1', 
          label = ' Select date', 
          value = max_date,
          min = min_date, 
          max = max_date,
          format="yyyy-mm-dd")
```

```{r select-input10}

 selectInput(inputId = 'si_count5', label = 'Select variable',
             choices = c("Total Confirmed Cases", "Total Confirmed Deaths", "Total Confirmed Recovered",
                         "Case Fatality Rate CFR","Case Recovered Rate CRR", "Cases per million",
                         "Deaths per million", "Recovered per million"), 
             selected = "Total Confirmed Cases", multiple = FALSE)
```

```{r select-input11}

 selectInput(inputId = 'si_count6', label = 'Select Colour Palette',
             choices = c("Viridis", "Reds", "Blues", "Greens"), 
             selected = "Viridis", multiple = FALSE)
```

Column
------------------------------------------------------------------

### **Regions map** 

```{r}

renderLeaflet({

World_count1=World_count  
  
region_map_date<-input$si_1
#region_map_date<-curr_date

Var_graph_reg<-input$si_count5
#Var_graph_reg<-"Case Fatality Rate CFR"

Var_col_palette<-input$si_count6

if (Var_col_palette=="Viridis"){
  Var_col_palette<-c("viridis")
}

if (Var_graph_reg=="Total Confirmed Cases"){
World_count1$reg_tot_cases<-as.numeric(NA)  
}
if (Var_graph_reg=="Total Confirmed Deaths"){
World_count1$reg_tot_deaths<-as.numeric(NA) 
}
if (Var_graph_reg=="Total Confirmed Recovered"){
World_count1$reg_tot_recovered<-as.numeric(NA)
}
if (Var_graph_reg=="Case Fatality Rate CFR"){
World_count1$CFR<-as.numeric(NA)
}
if (Var_graph_reg=="Case Recovered Rate CRR"){
World_count1$CRR<-as.numeric(NA)
}
if (Var_graph_reg=="Cases per million"){
World_count1$cases_per_million<-as.numeric(NA)
}
if (Var_graph_reg=="Deaths per million"){
World_count1$deaths_per_million<-as.numeric(NA)
}
if (Var_graph_reg=="Recovered per million"){
World_count1$recov_per_million<-as.numeric(NA)
}

data_region_covid<-data1 %>% 
  filter(date==region_map_date) %>% 
  group_by(region) %>%
  summarise(suma_cases=sum(total_cases), 
            suma_deaths=sum(total_deaths), 
            suma_recov=sum(total_recovered), 
            suma_populat=sum(population),n())

data_region_covid<-mutate(data_region_covid, 
                          CFR=(suma_deaths/suma_cases)*100, 
                          CRR=(suma_recov/suma_cases)*100,
                          cases_per_million=(suma_cases*1000000)/suma_populat,
                          deaths_per_million=(suma_deaths*1000000)/suma_populat,
                          recov_per_million=(suma_recov*1000000)/suma_populat) 

data_region_cont<-select(data1, date, iso_code, country, region) %>%
  filter(date==region_map_date)

data_region_cont<-left_join(data_region_cont, data_region_covid, by="region")

 for (i in 1:nrow(data_region_cont)){
    
   count_name=as.character(data_region_cont[i, 3])
    if (count_name != "Bonaire, Sint Eustatius and Saba"
     & count_name != "Channel Islands"
     & count_name != "Guadeloupe"
     & count_name != "French Guiana"
     & count_name != "Martinique"
     & count_name != "Mayotte"
     & count_name != "West Bank and Gaza"
     & count_name != "Reunion"){
      
   if (Var_graph_reg=="Total Confirmed Cases"){ 
   World_count1[which(World_count1$country==count_name), 7]=data_region_cont[i,5]
   }
   if (Var_graph_reg=="Total Confirmed Deaths"){   
   World_count1[which(World_count1$country==count_name), 7]=data_region_cont[i,6]
   }
   if (Var_graph_reg=="Total Confirmed Recovered"){   
   World_count1[which(World_count1$country==count_name), 7]=data_region_cont[i,7]
   }
   if (Var_graph_reg=="Case Fatality Rate CFR"){   
   World_count1[which(World_count1$country==count_name), 7]=round(data_region_cont[i,10], digits = 2)
   }
   if (Var_graph_reg=="Case Recovered Rate CRR"){   
   World_count1[which(World_count1$country==count_name), 7]=round(data_region_cont[i,11], digits = 2)
   }
   if (Var_graph_reg=="Cases per million"){   
   World_count1[which(World_count1$country==count_name), 7]=round(data_region_cont[i,12], digits = 2)
   }
   if (Var_graph_reg=="Deaths per million"){   
   World_count1[which(World_count1$country==count_name), 7]=round(data_region_cont[i,13], digits = 2)
   }
   if (Var_graph_reg=="Recovered per million"){   
   World_count1[which(World_count1$country==count_name), 7]=round(data_region_cont[i,14], digits = 2)
   }
 } else {}
 } 
   
#World_count1<-left_join(World_count, data_region_cont, by="country")
#World_count1<-left_join(World_count, data_region_cont, by="country")

   if (Var_graph_reg=="Total Confirmed Cases"){ 
      palnumeric <- colorBin(Var_col_palette, domain = World_count1$reg_tot_cases, bins=10, pretty=TRUE, alpha = F, reverse = F)
      popup <- paste0("<b>", "Region: ", "</b>", as.character(World_count1$REGION_WB), 
                      "<br>", "<b>", "Confirmed Cases: ", "</b>", World_count1$reg_tot_cases)
      col_obj<-World_count1$reg_tot_cases
   }
   if (Var_graph_reg=="Total Confirmed Deaths"){ 
      palnumeric <- colorBin(Var_col_palette, domain = World_count1$reg_tot_deaths, bins=10, pretty=TRUE, alpha = F, reverse = F)
      popup <- paste0("<b>", "Region: ", "</b>", as.character(World_count1$REGION_WB), 
                      "<br>", "<b>", "Confirmed Deaths: ", "</b>", World_count1$reg_tot_deaths)
      col_obj<-World_count1$reg_tot_deaths
   }
   if (Var_graph_reg=="Total Confirmed Recovered"){ 
      palnumeric <- colorBin(Var_col_palette, domain = World_count1$reg_tot_recovered, bins=10, pretty=TRUE, alpha = F, reverse = F)
      popup <- paste0("<b>", "Region: ", "</b>", as.character(World_count1$REGION_WB), 
                      "<br>", "<b>", "Confirmed Recovered: ", "</b>", World_count1$reg_tot_recovered)
      col_obj<-World_count1$reg_tot_recovered
   }
   if (Var_graph_reg=="Case Fatality Rate CFR"){ 
      palnumeric <- colorBin(Var_col_palette, domain = World_count1$CFR, bins=10, pretty=TRUE, alpha = F, reverse = F)
      popup <- paste0("<b>", "Region: ", "</b>", as.character(World_count1$REGION_WB),
                      "<br>", "<b>", "CFR: ", "</b>", World_count1$CFR)
      col_obj<-World_count1$CFR
   }
   if (Var_graph_reg=="Case Recovered Rate CRR"){ 
      palnumeric <- colorBin(Var_col_palette, domain = World_count1$CRR, bins=10, pretty=TRUE, alpha = F, reverse = F)
      popup <- paste0("<b>", "Region: ", "</b>", as.character(World_count1$REGION_WB), 
                      "<br>", "<b>", "CRR: ", "</b>", World_count1$CRR)
      col_obj<-World_count1$CRR
   }
   if (Var_graph_reg=="Cases per million"){ 
      palnumeric <- colorBin(Var_col_palette, domain = World_count1$cases_per_million, bins=10, pretty=TRUE, alpha = F, reverse = F)
      popup <- paste0("<b>", "Region: ", "</b>", as.character(World_count1$REGION_WB), 
                      "<br>", "<b>", "Cases per million: ", "</b>", World_count1$cases_per_million)
      col_obj<-World_count1$cases_per_million
   }
   if (Var_graph_reg=="Deaths per million"){ 
      palnumeric <- colorBin(Var_col_palette, domain = World_count1$deaths_per_million, bins=10, pretty=TRUE, alpha = F, reverse = F)
      popup <- paste0("<b>", "Region: ", "</b>", as.character(World_count1$REGION_WB), 
                      "<br>", "<b>", "Deaths per million: ", "</b>", World_count1$deaths_per_million)
      col_obj<-World_count1$deaths_per_million
   }
   if (Var_graph_reg=="Recovered per million"){ 
      palnumeric <- colorBin(Var_col_palette, domain = World_count1$recov_per_million, bins=10, pretty=TRUE, alpha = F, reverse = F)
      popup <- paste0("<b>", "Region: ", "</b>", as.character(World_count1$REGION_WB), 
                      "<br>", "<b>", "Recovered per million ", "</b>", World_count1$recov_per_million)
      col_obj<-World_count1$recov_per_million
   }

World_count1<-cbind(World_count1,col_obj)

leaflet(options = leafletOptions(dragging=TRUE,
                                 minZoom = 2.2,
                                 maxZoom = 18,
                                 preferCanvas = TRUE)) %>% 
  addTiles(group = "OMS (default)") %>%
  addProviderTiles("CartoDB", group="CartoDB", 
                   options = providerTileOptions(updateWhenZooming=FALSE,
                                                 updateWhenIdle = TRUE)) %>% 
  setView(lng = 0, lat=40, zoom= 2.2) %>% 

  addPolygons(data=World_count1,
              color = "#444444" ,
              weight = 1, 
              smoothFactor = 0.5,
              opacity = 1.0,
              fillOpacity = 0.5,
              fillColor = ~palnumeric(World_count1$col_obj),    # Color de llenado
              group = (Var_graph_reg),                  
              highlightOptions = highlightOptions(color = "white", weight = 2,
                                                  bringToFront = TRUE), #highlight cuando pasas el cursor
              label = ~World_count1$REGION_WB,                                  # etiqueta cuando pasas el cursor
              labelOptions = labelOptions(direction = "auto"),
              popup = popup) %>%        # mostrar el popup
          addLegend(position = "bottomleft", pal = palnumeric, values = World_count1$col_obj,
                    group = (Var_graph_reg),title= (Var_graph_reg), opacity = 1) %>% 
  addGraticule(interval = 20, style = list(color = "gray", weight = 1), group="Graticule") %>% 
  addLayersControl(
    baseGroups = c("OMS (default)", "CartoDB"),
    overlayGroups = c("Graticule"),    
    options = layersControlOptions(collapsed = TRUE)) %>% 
  
  addMiniMap(tiles = providers$Esri.WorldStreetMap,
    toggleDisplay = TRUE)%>% 
    addScaleBar(position = "bottomright", options = scaleBarOptions(maxWidth = 100, 
                                                                    metric = TRUE,
                                                                    updateWhenIdle = TRUE))
})

```


Summary {data-icon="fa-list" data-orientation=columns data-navmenu="Countries"}
======================================================================================

Column {.sidebar}
------------------------------------------------------------------
```{r}
dateInput(inputId = 'si_for_date', 
          label = ' Select date', 
          value = max_date,
          min = min_date, 
          max = max_date,
          format="yyyy-mm-dd")
```


```{r select-input5}
 list_var<-c("cumulative cases", "cumulative deaths", "cumulative recovered")
 
 selectInput(
   inputId = 'si_var_a', label = 'Select variable',
   choices = list_var)
```

```{r select-input6}

 list_var<-c("treemap", "sunburst")

 selectInput(
   inputId = 'si_var_b', label = 'Select chart type',
   choices = list_var)
```

```{r slider-input6}

max_cases_curr_date<- data1 %>% 
  filter(date==curr_date)

vect_casos<-max_cases_curr_date[, "total_cases"]  
max_cas=max(vect_casos)

 sliderInput(inputId = 'sli_6', label = 'Range cummulative CASES',
             min=0, max=max_cas, value=max_cas)
```

```{r slider-input7}

max_deaths_curr_date<- data1 %>% 
  filter(date==curr_date)

vect_deaths<-max_deaths_curr_date[, "total_deaths"]  
max_det=max(vect_deaths)

 sliderInput(inputId = 'sli_7', label = 'Range cummulative DEATHS',
             min=0, max=max_det, value=max_det)
```

```{r slider-input8}

max_recovered_curr_date<- data1 %>% 
  filter(date==curr_date)

vect_recovered<-max_recovered_curr_date[, "total_recovered"]  
max_rec=max(vect_recovered)

 sliderInput(inputId = 'sli_8', label = 'Range cummulative RECOVERED',
             min=0, max=max_rec, value=max_rec)
```


```{r text-input1}
textInput(inputId= 'text_Id_1', label='"A", bar width for histogram, (Apply to Density bars & frequency Table) Confirmed CASES', value = c("50000"))

```

```{r text-input2}
textInput(inputId= 'text_Id_2', label='"A", bar width for histogram, (Apply to Density bars & frequency Table) Confirmed DEATHS', value = c("500"))

```

```{r text-input3}
textInput(inputId= 'text_Id_3', label='"A", bar width for histogram, (Apply to Density bars & frequency Table) Confirmed RECOVERED', value = c("20000"))

```

Row {.tabset .tabset-fade}
---------------------------------------------------------------------------------------

### **Country & Region charts**
```{r}

renderHighchart({

date_for_chart<-input$si_for_date
#date_for_chart<-curr_date

date_variable<-input$si_var_a
chart_type<-input$si_var_b
#date_variable<-c("cumulative cases")

Country_chart_data<- data1 %>% 
  filter(date==date_for_chart)

 if (date_variable=="cumulative cases"){
       varsize<-"total_cases"
 } else {}

 if (date_variable=="cumulative deaths"){
       varsize<-"total_deaths"
 } else {}
 if (date_variable=="cumulative recovered"){
       varsize<-"total_recovered"
 } else {}

tm<- data_to_hierarchical(data=Country_chart_data,
                     group_vars = c("region","country"),
                     size_var = c(varsize),
                     colors = getOption("highcharter.color_palette"))

hchart(tm, type = chart_type) %>% 
hc_title(text= paste("Confirmed", date_variable, "by countries and regions,", chart_type,". Date:", date_for_chart), 
           align="left",
           useHTML=TRUE) %>% 
 hc_subtitle(text="<i>Data source: https://github.com/CSSEGISandData/COVID-19/tree/master/csse_covid_19_data/csse_covid_19_time_series", 
           align="left",
           useHTML=TRUE) %>%
 hc_legend(enabled = TRUE) %>% 
   hc_exporting(enabled = TRUE,
             filename="Countries_variables",
             formAttribute=list(target="_black"),
             buttons=list(contextButton=list(theme=list(fill="transparent")))) %>%  # enable export
hc_credits(enabled = TRUE, text = "Dr. Eric Cabrera Estupinan",
           href = "http://www.htmlwidgets.org/")
})

```

Column {.tabset}
--------------------------------------------------------------------------------------

### **Histogram (IAH)**

```{r, fig.keep='none'}

renderHighchart({

date_for_chart<-input$si_for_date
#date_for_chart<-curr_date

date_variable<-input$si_var_a
#date_variable<-c("cumulative cases")

 if (date_variable=="cumulative cases"){
     data1<- data1 %>%
       mutate(Col_obj=total_cases)  
     var_hist<-input$sli_6
       #varsize1<-"total_cases"
 } else {}

 if (date_variable=="cumulative deaths"){
     data1<- data1 %>%
       mutate(Col_obj=total_deaths) 
     var_hist<-input$sli_7
       #varsize1<-"total_deaths"
 } else {}
 if (date_variable=="cumulative recovered"){
     data1<- data1 %>%
       mutate(Col_obj=total_recovered) 
     var_hist<-input$sli_8
       #varsize1<-"total_recovered"
 } else {}

hist_sel_date = data1 %>%
  filter(date==date_for_chart) %>% 
  select(Col_obj)

#hist_sel_date_org<-hist_sel_date
hist_sel_date<- hist_sel_date %>% 
  subset(Col_obj<=var_hist)

# datos<-hist_sel_date[, "Col_obj"]
# datos_org<-rev(sort(datos$Col_obj,decreasing=TRUE))

#------------------------Histogram----------
hchart(hist_sel_date$Col_obj, 
       color = "#B71C1C", 
       name = "Countries frequency") %>% 
  hc_xAxis(title = list(text=paste("Total confirmed", date_variable)),
         labels=list(format= "{value:,.0f}")) %>% 
hc_yAxis(title = list(text="Number of countries (Absolute frequency)"),
           labels=list(format= "{value:,.0f}"),
           opposite=FALSE) %>%
hc_title(text=paste("Absolute frequency of confirmed", date_variable, "by countries. Date:", date_for_chart),
         align="left",
         useHTML=TRUE) %>%
hc_subtitle(text="Internal algorithm of Highcharter (IAH) <br> <i>Data source: https://github.com/CSSEGISandData/COVID-19/tree/master/csse_covid_19_data/csse_covid_19_time_series", 
            align="left",
            useHTML=TRUE) %>% 
hc_legend(enabled = TRUE,
          align = "right", 
          verticalAlign = "top",
          layout = "horizontal") %>%  
     hc_exporting(enabled = TRUE,
             filename="Histogram_countries",
             formAttribute=list(target="_black"),
             buttons=list(contextButton=list(theme=list(fill="transparent")))) %>%  # enable export
hc_tooltip(crosshairs=TRUE,
           bacgroundColor="transparent") %>% 
hc_credits(enabled = TRUE, text = "Dr. Eric Cabrera Estupinan",
           href = "http://www.htmlwidgets.org/")
#---------------------------------------------------------

})

```

### **Density (IAH)**

```{r, fig.keep='none'}

renderHighchart({

date_for_chart<-input$si_for_date
#date_for_chart<-curr_date

date_variable<-input$si_var_a
#date_variable<-c("cumulative cases")

 if (date_variable=="cumulative cases"){
     data1<- data1 %>%
       mutate(Col_obj=total_cases)
     var_hist<-input$sli_6
       #varsize1<-"total_cases"
 } else {}

 if (date_variable=="cumulative deaths"){
     data1<- data1 %>%
       mutate(Col_obj=total_deaths)
     var_hist<-input$sli_7
       #varsize1<-"total_deaths"
 } else {}
 if (date_variable=="cumulative recovered"){
     data1<- data1 %>%
       mutate(Col_obj=total_recovered) 
     var_hist<-input$sli_8
       #varsize1<-"total_recovered"
 } else {}

hist_sel_date = data1 %>%
  filter(date==date_for_chart) %>% 
  select(Col_obj)

hist_sel_date<- hist_sel_date %>% 
  subset(Col_obj<=var_hist)

#------------------------Histogram----------
hchart(density(hist_sel_date$Col_obj),
       type ="area",
       color = "red", 
       name = "Countries frequency") %>% 
  hc_xAxis(title = list(text=paste("Total confirmed", date_variable)),
         labels=list(format= "{value:,.0f}")) %>% 
hc_yAxis(title = list(text="Density)"),
           labels=list(format= "{value:,.7f}"),
           opposite=FALSE) %>%
hc_title(text=paste("Density of confirmed", date_variable, "by countries. Date:", date_for_chart),
         align="left",
         useHTML=TRUE) %>%
hc_subtitle(text="Internal algorithm of Highcharter (IAH) <br> <i>Data source: https://github.com/CSSEGISandData/COVID-19/tree/master/csse_covid_19_data/csse_covid_19_time_series", 
            align="left",
            useHTML=TRUE) %>% 
hc_legend(enabled = TRUE,
          align = "right", 
          verticalAlign = "top",
          layout = "horizontal") %>%  
     hc_exporting(enabled = TRUE,
             filename="Density_countries",
             formAttribute=list(target="_black"),
             buttons=list(contextButton=list(theme=list(fill="transparent")))) %>%  # enable export
hc_tooltip(crosshairs=TRUE,
           bacgroundColor="transparent") %>% 
hc_credits(enabled = TRUE, text = "Dr. Eric Cabrera Estupinan",
           href = "http://www.htmlwidgets.org/")
#-------------------------------------------
})

```

### **Density bars**

```{r}

renderHighchart({

date_for_chart<-input$si_for_date
#date_for_chart<-curr_date

date_variable<-input$si_var_a
#date_variable<-c("cumulative cases")

 if (date_variable=="cumulative cases"){
     data1<- data1 %>%
       mutate(Col_obj=total_cases) 
     var_hist<-input$sli_6
     A<-input$text_Id_1
     A<-as.numeric(A)
       #varsize1<-"total_cases"
 } else {}

 if (date_variable=="cumulative deaths"){
     data1<- data1 %>%
       mutate(Col_obj=total_deaths)
     var_hist<-input$sli_7
     A<-input$text_Id_2
     A<-as.numeric(A)
       #varsize1<-"total_deaths"
 } else {}
 if (date_variable=="cumulative recovered"){
     data1<- data1 %>%
       mutate(Col_obj=total_recovered)
     var_hist<-input$sli_8
     A<-input$text_Id_3
     A<-as.numeric(A)
       #varsize1<-"total_recovered"
 } else {}

hist_sel_date = data1 %>%
  filter(date==date_for_chart) %>% 
  select(Col_obj)

hist_sel_date<- hist_sel_date %>% 
  subset(Col_obj<=var_hist)

datos<-hist_sel_date[, "Col_obj"]
datos_org<-rev(sort(datos$Col_obj,decreasing=TRUE))

N<-length(datos_org)
R=max(datos_org)-min(datos_org) #Recorrido o rango

#A=50000
k=round(R/A)
L=A*(0:k)

#--------Tabla de frecuencia--------------#
  L=(0)+A*(0:k) #Extremos de los intervalos
  x_int=cut(datos_org, breaks=L, right=FALSE, dig.lab=5)
  intervalos=levels(x_int)
  marcas=(L[1]+L[2])/2+A*(0:(k-1)) #Marcas de clase
  f_abs=as.vector(table(x_int)) #Frecuencias absolutas
  f_rel=round(f_abs/length(datos_org), digits = 3) #Frecuencias relativas
  f_abs_cum=cumsum(f_abs) #Frecuencias absolutas acumuladas
  f_rel_cum=round(cumsum(f_rel),digits = 3) #Frecuencias relativas acumuladas
  Density=f_rel/A #Densidades
  Density_cum=cumsum(Density) #Densidades acumuladas
  tabla_x=data.frame(intervalos, marcas, f_abs, f_abs_cum, f_rel, f_rel_cum, Density, Density_cum)
  #tabla_x
#------------------------------------------

tabla_densid<-tabla_x
tabla_densid<-mutate(tabla_densid, Fabs="Abs freq", 
                     Frela="Rel freq", Intervalo="Interval", Densidad="Density", Density_acum= "Density_cum")

highchart () %>%
  hc_add_series(data= tabla_densid,
                type="column",
                name="Bar density",
                hcaes(x=marcas, y=Density),
                color="darkred") %>%
  hc_add_series(data= tabla_densid,
                type="spline",
                name="Area density",
                hcaes(x=marcas, y=Density),
                color="#B71C1C") %>%
hc_xAxis(title = list(text=paste("Total confirmed", date_variable)),
       labels=list(format= "{value:,.0f}")) %>%
hc_yAxis(title = list(text="Density"),
         labels=list(format= "{value:,.7f}"),
         opposite=FALSE) %>%
hc_title(text=paste("Density of confirmed", date_variable, "by countries. Date:", date_for_chart),
         align="left",
         useHTML=TRUE) %>%
  hc_subtitle(text="Author's method <br> <i>Data source: https://github.com/CSSEGISandData/COVID-19/tree/master/csse_covid_19_data/csse_covid_19_time_series",
            align="left",
            useHTML=TRUE) %>%
hc_legend(enabled = TRUE,
          align = "right",
          verticalAlign = "top",
          layout = "horizontal") %>%
hc_exporting(enabled = TRUE,
             filename="Density_bar_countries",
             formAttribute=list(target="_black"),
             buttons=list(contextButton=list(theme=list(fill="transparent")))) %>%  # enable export
hc_tooltip(shared = FALSE,
           crosshairs=TRUE,
           bacgroundColor="transparent",
           pointFormat = "{point.Intervalo}: {point.intervalos}<br> {point.Fabs}: {point.f_abs}<br> {point.Frela}: {point.f_rel}<br> {point.Densidad}: {point.Density}<br>") %>%
hc_credits(enabled = TRUE, text = "Dr. Eric Cabrera Estupinan",
           href = "http://www.htmlwidgets.org/")

})

```

### **Frequency table**

```{r}

renderDT({  
  
date_for_chart<-input$si_for_date
#date_for_chart<-curr_date

date_variable<-input$si_var_a
#date_variable<-c("cumulative cases")

 if (date_variable=="cumulative cases"){
     data1<- data1 %>%
       mutate(Col_obj=total_cases)
     var_hist<-input$sli_6
     A<-input$text_Id_1
     A<-as.numeric(A)
       #varsize1<-"total_cases"
 } else {}

 if (date_variable=="cumulative deaths"){
     data1<- data1 %>%
       mutate(Col_obj=total_deaths)
     var_hist<-input$sli_7
     A<-input$text_Id_2
     A<-as.numeric(A)
       #varsize1<-"total_deaths"
 } else {}
 if (date_variable=="cumulative recovered"){
     data1<- data1 %>%
       mutate(Col_obj=total_recovered)
     var_hist<-input$sli_8
     A<-input$text_Id_3
     A<-as.numeric(A)
       #varsize1<-"total_recovered"
 } else {}

hist_sel_date = data1 %>%
  filter(date==date_for_chart) %>% 
  select(date, country, Col_obj)

hist_sel_date<- hist_sel_date %>% 
  subset(Col_obj<=var_hist)

datos<-hist_sel_date[, "Col_obj"]
datos_org<-rev(sort(datos$Col_obj,decreasing=TRUE))

N<-length(datos_org)
R=max(datos_org)-min(datos_org) #Recorrido o rango

#A=50000
k=round(R/A)
L=A*(0:k)

#--------Tabla de frecuencia--------------#
  L=(0)+A*(0:k) #Extremos de los intervalos
  x_int=cut(datos_org, breaks=L, right=FALSE, dig.lab=5)
  intervalos=levels(x_int)
  marcas=(L[1]+L[2])/2+A*(0:(k-1)) #Marcas de clase
  f_abs=as.vector(table(x_int)) #Frecuencias absolutas
  f_rel=round(f_abs/length(datos_org), digits = 3) #Frecuencias relativas
  f_abs_cum=cumsum(f_abs) #Frecuencias absolutas acumuladas
  f_rel_cum=round(cumsum(f_rel),digits = 3) #Frecuencias relativas acumuladas
  Density=f_rel/A #Densidades
  Density_cum=cumsum(Density) #Densidades acumuladas
  tabla_x=data.frame(intervalos, marcas, f_abs, f_abs_cum, f_rel, f_rel_cum, Density, Density_cum)
  #tabla_x
#------------------------------------------

tabla_densid<-tabla_x
tabla_densid<-mutate(tabla_densid, Fabs="Abs freq", 
                     Frela="Rel freq", Intervalo="Interval", Densidad="Density", Density_acum= "Density_cum")
 
datatable(tabla_x,
          caption = paste("Total confirmed", date_variable, "frequency table"),
          rownames = T,
          filter = "top",
          extensions= c('Select','Buttons', 'ColReorder', 'KeyTable', 'Responsive', 'Scroller'), 
          options = list(pageLength=25, 
                         dom = 'Blfrtip',
                         buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                         lengthMenu=list(c(10, 25, 50, -1), c(10, 25, 50, "All")),
                         colReorder = TRUE),
 selection = 'none')  
  
})

```

### **Cumulative Density**
```{r}

renderHighchart({

date_for_chart<-input$si_for_date
#date_for_chart<-curr_date

date_variable<-input$si_var_a
#date_variable<-c("cumulative cases")

 if (date_variable=="cumulative cases"){
     data1<- data1 %>%
       mutate(Col_obj=total_cases)
     var_hist<-input$sli_6
     A<-input$text_Id_1
     A<-as.numeric(A)
       #varsize1<-"total_cases"
 } else {}

 if (date_variable=="cumulative deaths"){
     data1<- data1 %>%
       mutate(Col_obj=total_deaths)
     var_hist<-input$sli_7
     A<-input$text_Id_2
     A<-as.numeric(A)
       #varsize1<-"total_deaths"
 } else {}
 if (date_variable=="cumulative recovered"){
     data1<- data1 %>%
       mutate(Col_obj=total_recovered)
     var_hist<-input$sli_8
     A<-input$text_Id_3
     A<-as.numeric(A)
       #varsize1<-"total_recovered"
 } else {}

hist_sel_date = data1 %>%
  filter(date==date_for_chart) %>% 
  select(date, country, Col_obj)

hist_sel_date<- hist_sel_date %>% 
  subset(Col_obj<=var_hist)

datos<-hist_sel_date[, "Col_obj"]
datos_org<-rev(sort(datos$Col_obj,decreasing=TRUE))

N<-length(datos_org)
R=max(datos_org)-min(datos_org) #Recorrido o rango

#A=50000
k=round(R/A)
L=A*(0:k)

#--------Tabla de frecuencia--------------#
  L=(0)+A*(0:k) #Extremos de los intervalos
  x_int=cut(datos_org, breaks=L, right=FALSE, dig.lab=5)
  intervalos=levels(x_int)
  marcas=(L[1]+L[2])/2+A*(0:(k-1)) #Marcas de clase
  f_abs=as.vector(table(x_int)) #Frecuencias absolutas
  f_rel=round(f_abs/length(datos_org), digits = 3) #Frecuencias relativas
  f_abs_cum=cumsum(f_abs) #Frecuencias absolutas acumuladas
  f_rel_cum=round(cumsum(f_rel),digits = 3) #Frecuencias relativas acumuladas
  Density=f_rel/A #Densidades
  Density_cum=cumsum(Density) #Densidades acumuladas
  tabla_x=data.frame(intervalos, marcas, f_abs, f_abs_cum, f_rel, f_rel_cum, Density, Density_cum)
  #tabla_x
#------------------------------------------

tabla_densid<-tabla_x
tabla_densid<-mutate(tabla_densid, Fabs="Abs freq", 
                     Frela="Rel freq", Intervalo="Interval", Densidad="Density", Density_acum= "Density_cum")

highchart () %>%
  hc_add_series(data= tabla_densid, 
                type="line",
                name="Cumulative Density",
                hcaes(x=marcas, y=Density_cum),
                color="#B71C1C") %>% 
  hc_xAxis(title = list(text=paste("Total confirmed", date_variable)),
         labels=list(format= "{value:,.0f}")) %>% 
  hc_yAxis(title = list(text="Cumulative Density"),
           labels=list(format= "{value:,.7f}"),
           opposite=FALSE) %>%
hc_title(text=paste("Cumulative Density of confirmed", date_variable, "by countries. Date:", date_for_chart),  
         align="left",
         useHTML=TRUE) %>%
  hc_subtitle(text="Author's method <br> <i>Data source: https://github.com/CSSEGISandData/COVID-19/tree/master/csse_covid_19_data/csse_covid_19_time_series", 
            align="left",
            useHTML=TRUE) %>% 
hc_legend(enabled = TRUE,
          align = "right", 
          verticalAlign = "top",
          layout = "horizontal") %>%  
  hc_exporting(enabled = TRUE,
             filename="Cumulative_Density",
             formAttribute=list(target="_black"),
             buttons=list(contextButton=list(theme=list(fill="transparent")))) %>%  # enable export
hc_tooltip(shared = FALSE,
           crosshairs=TRUE,
           bacgroundColor="transparent",
           pointFormat = "{point.Intervalo}: {point.intervalos}<br> {point.Density_acum}: {point.Density_cum}<br> ") %>% 
hc_credits(enabled = TRUE, text = "Dr. Eric Cabrera Estupinan",
           href = "http://www.htmlwidgets.org/")
})
```



Pick a country {data-icon="fa-line-chart" data-orientation=rows data-navmenu="Countries"}
==========================================================================================

Column {.sidebar}
------------------------------------------------------------------

```{r select-input4}
count_list_main<-data1 %>% select(country) %>% distinct(country)
 count_list_main<-as.character(count_list_main$country)
 
 selectInput(
   inputId = 'si_count_main', label = ' Select a Country',
   choices = count_list_main, selected = "US")
```

```{r select-input29}

dateInput(inputId = 'si_reg_2', 
          label = 'Select date', 
          value = max_date,
          min = min_date, 
          max = max_date,
          format="yyyy-mm-dd")
```

Row
---------------------------------------------------------------------------------------

### **Updated**

```{r}
valueBox(paste(curr_date),
         color="warning")
```

### **Total confirmed cases** 

```{r}
renderValueBox({

country_main_sel<-input$si_count_main
date_count<-input$si_reg_2
valueBox(data1 %>% filter(date==date_count) %>% 
           filter(country==country_main_sel) %>% 
           summarise(sum(total_cases)),
         icon = "fa-users")
})
```

### **New confirmed cases**

```{r}
renderValueBox({

country_main_sel<-input$si_count_main
date_count<-input$si_reg_2
valueBox(data1 %>% filter(date==date_count) %>%
           filter(country==country_main_sel) %>% 
           summarise(sum(new_cases)),
         icon = "fa-ambulance")
})
```

### **Total confirmed deaths**

```{r}
renderValueBox({

country_main_sel<-input$si_count_main 
date_count<-input$si_reg_2
valueBox(data1 %>% filter(date==date_count) %>%
           filter(country==country_main_sel) %>%
           summarise(sum(total_deaths)),
         icon = "fa-hospital",
         color="red")
})  
```

### **New confirmed deaths**

```{r}
renderValueBox({

country_main_sel<-input$si_count_main   
date_count<-input$si_reg_2
valueBox(data1 %>% filter(date==date_count) %>%
           filter(country==country_main_sel) %>%
           summarise(sum(new_deaths)),
         icon = "fa-hospital",
         color="red")
})  
```

### **Total confirmed recovered**

```{r}
renderValueBox({
 
country_main_sel<-input$si_count_main 
date_count<-input$si_reg_2
valueBox(data1 %>% filter(date==date_count) %>%
           filter(country==country_main_sel) %>%
           summarise(sum(total_recovered)),
         icon = "fa-heartbeat",
         color="green")
})  
```

### **New confirmed recovered**

```{r}
renderValueBox({
  
country_main_sel<-input$si_count_main 
date_count<-input$si_reg_2
valueBox(data1 %>% filter(date==date_count) %>%
           filter(country==country_main_sel) %>%
           summarise(sum(new_recovered)),
         icon = "fa-heartbeat",
         color="green")
})
```

Row
---------------------------------------------------------------------------------------

### **Country Case Fatality Rate CFR (%)**

```{r}
renderGauge({

country_main_sel<-input$si_count_main 
date_count<-input$si_reg_2
ff1<-data1 %>%
  filter(date==date_count) %>% filter(country==country_main_sel) %>%
  summarise(sum(total_cases))

ff2<-data1 %>%
  filter(date==date_count) %>% filter(country==country_main_sel) %>%
  summarise(sum(total_deaths))

let_maincount<-as.numeric((ff2/ff1)*100)
gauge(round(let_maincount,
            digits = 2),
            min=0,
            max=10,
            gaugeSectors(success = c(0, 3),
                         warning=c(3, 7),
                         danger=c(7, 10),
                         colors=c('green', 'yellow', 'red')))
})
```

### **Country Case Recovered Rate CRR (%)**

```{r}
renderGauge({

country_main_sel<-input$si_count_main
date_count<-input$si_reg_2
ff1<-data1 %>%
  filter(date==date_count) %>% filter(country==country_main_sel) %>%
  summarise(sum(total_cases))

ff3<-data1 %>% 
  filter(date==date_count) %>% filter(country==country_main_sel) %>%
  summarise(sum(total_recovered))

recov_maincount<-as.numeric((ff3/ff1)*100)
gauge(round(recov_maincount,
            digits = 2),
            min=0,
            max=100,
            gaugeSectors(success = c(60, 100),
                         warning=c(30, 60),
                         danger=c(0, 30),
                         colors=c('green', 'yellow', 'red')))
})
```


Row {.tabset .tabset-fade}
---------------------------------------------------------------------------------------

### **Country map**
```{r}

World_count3=World_count

 for (i in 1:nrow(row_data2)){
    
   count_name=as.character(row_data2[i, 2])
    if (count_name != "Bonaire, Sint Eustatius and Saba"
     & count_name != "Channel Islands"
     & count_name != "Guadeloupe"
     & count_name != "French Guiana"
     & count_name != "Martinique"
     & count_name != "Mayotte"
     & count_name != "West Bank and Gaza"
     & count_name != "Reunion"){
      
   World_count3[which(World_count3$country==count_name), 3]=row_data2[i,9]
   World_count3[which(World_count3$country==count_name), 4]=row_data2[i,10]
   World_count3[which(World_count3$country==count_name), 5]=row_data2[i,11]
 } else {}
 }   

renderLeaflet({

country_main_sel<-input$si_count_main 
#country_main_sel<-c("Zimbabwe")

nf<-which(World_count3$country==country_main_sel)
count_plot<-World_count3[nf, ]

leaflet(options = leafletOptions(dragging=TRUE,
                                 minZoom = 2.2,
                                 maxZoom = 18,
                                 preferCanvas = TRUE)) %>% 
  addTiles(group = "OMS (default)") %>%
  addProviderTiles("CartoDB", group="CartoDB", 
                   options = providerTileOptions(updateWhenZooming=FALSE,
                                                 updateWhenIdle = TRUE)) %>% 
  addPolygons(data = count_plot,
               fillColor = "blue", 
               color = "blue", 
               fillOpacity = .1,
               label = ~country) %>% 
  setView(lng = count_plot$Long , lat=count_plot$Lat, zoom=count_plot$zoom) %>% 
  addGraticule(interval = 20, style = list(color = "gray", weight = 1), group="Graticule") %>% 
  addLayersControl(baseGroups = c("OSM (default)", "CartoDB"),    
#  addLayersControl(baseGroups = c("OSM (default)", "CartoDB", "CartoDB.DarkMatter", "OpenTopoMap"),
    overlayGroups=c("Graticule"),
    options = layersControlOptions(collapsed = TRUE)) %>% 
  addMiniMap(tiles = providers$Esri.WorldStreetMap,
    toggleDisplay = TRUE)%>% 
    addScaleBar(position = "bottomright", options = scaleBarOptions(maxWidth = 100, 
                                                                    metric = TRUE,
                                                                    updateWhenIdle = TRUE)) %>% 
    addMeasure(position="bottomleft",
               primaryLengthUnit = "meters",
               primaryAreaUnit = "sqmeters",
               activeColor = "#3D535D",
               completedColor = "#7D4479",
               localization=de)
})

```

### **Cumulative variables TS**

```{r}

 renderHighchart({
 
 country_main_sel<-input$si_count_main 
# country_main_sel<-c("US")
 
 Main_count_data_var<-data1 %>% filter(country==country_main_sel) %>%
   select(date, country, total_cases, total_deaths, total_recovered)
 
 cols <- c(brewer.pal(7, "Set1"),"black")
 
 highchart (type="stock") %>%
   
 hc_add_series(data=Main_count_data_var,
                 name="Deaths",
                 type="area",
                 hcaes(x=date, y=total_deaths)) %>% 
 hc_add_series(data=Main_count_data_var,
                 name="Cases",
                 type="area",
                 hcaes(x=date, y=total_cases)) %>%    
 hc_add_series(data=Main_count_data_var,
                 name="Recovered",
                 type="area",
                 hcaes(x=date, y=total_recovered)) %>% 
 hc_title(text=paste("Cumulative total confirmed CASES, DEATHS & RECOVERED in:", country_main_sel,"(Time Serie, TS)"),
         align="left",
         useHTML=TRUE) %>%
hc_subtitle(text="<i>Data source: https://github.com/CSSEGISandData/COVID-19/tree/master/csse_covid_19_data/csse_covid_19_time_series",
            align="left",
            useHTML=TRUE) %>%
hc_legend(enabled = TRUE) %>%
     hc_exporting(enabled = TRUE,
             filename="Cumulative_variables_country_TS",
             formAttribute=list(target="_black"),
             buttons=list(contextButton=list(text="Export",
                                             theme=list(fill="transparent")))) %>%  # enable export
hc_colors(cols) %>%
hc_plotOptions(series = list(stacking = "normal",
                                marker = list(enabled = FALSE, symbol = "circle", size=1,
                                              states = list(hover = list(enabled = TRUE))),
                                lineWidth = 1,
                                lineColor="black")) %>%
hc_xAxis(title = list(text="time (days)"),
           type="datetime") %>%
hc_yAxis(title = list(text="Confirmed cases, deaths & recovered"),
         type="number",
         labels=list(format= "{value:,.0f}"),
         opposite=FALSE) %>%
hc_tooltip(shared = FALSE,
           crosshairs=TRUE,
           borderWidth = 2,
           bacgroundColor="transparent") %>%
hc_credits(enabled = TRUE, text = "Dr. Eric Cabrera Estupinan",
            href = "http://www.htmlwidgets.org/") %>%
hc_rangeSelector(selected = 4) %>%
hc_navigator( #outlineColor = "gray",
              outlineWidth = 2,
              series = list(color = "red",
                            lineWidth = 2,
                            type = "areaspline", # you can change the type
                            fillColor = "rgba(255, 0, 0, 0.2)"))

 })

```

### **Cumulative variables per 100000 inhabitant TS**

```{r}

renderHighchart({

country_main_sel<-input$si_count_main 
Main_count_data_inhab<-data1 %>% filter(country==country_main_sel) %>%
  select(date, factor1, factor2, factor3)


# set color palette
cols <- brewer.pal(7, "Set1")
#cols <- c("blue","green","red")

highchart (type="stock") %>%

  hc_add_series(data=Main_count_data_inhab,
                name="Deaths per 100000 inhab",
                type="line", 
                hcaes(x=date, y=round(factor2, digits = 2))) %>%    
  hc_add_series(data=Main_count_data_inhab, 
                name="Cases per 100000 inhab",
                type="line", 
                hcaes(x=date, y=round(factor1, digits = 2))) %>%   
  hc_add_series(data=Main_count_data_inhab,
                name="Recovered per 100000 inhab",
                type="line", 
                hcaes(x=date, y=round(factor3, digits = 2))) %>%
hc_title(text=paste("Cumulative total confirmed: CASES, DEATHS and RECOVERED per 100000 inhab in", country_main_sel, "(Time Serie, TS)"),
         align="left",
         useHTML=TRUE) %>%
hc_subtitle(text="<i>Data source: https://github.com/CSSEGISandData/COVID-19/tree/master/csse_covid_19_data/csse_covid_19_time_series", 
            align="left",
            useHTML=TRUE) %>%   
hc_legend(enabled = TRUE) %>% 
     hc_exporting(enabled = TRUE,
             filename="Cumulative_variables_country_TS_houndredThausand",
             formAttribute=list(target="_black"),
             buttons=list(contextButton=list(text="Export",
                                             theme=list(fill="transparent")))) %>%  # enable export
hc_colors(cols) %>%
hc_plotOptions(series = list(stacking = NULL,
                               marker = list(enabled = TRUE, symbol = "circle", size=1,
                                             states = list(hover = list(enabled = TRUE))),
                               lineWidth = 2,
                               fillColor="red")) %>%
hc_xAxis(title = list(text="time (days)"),
           type="datetime") %>%
hc_yAxis(title = list(text="Cases, Deaths and Recovered per 100000 inhab"),
           labels=list(format= "{value:,.0f}"),
           opposite=FALSE) %>%
hc_tooltip(shared = FALSE,
             crosshairs=TRUE,
             bacgroundColor="transparent") %>% 
hc_credits(enabled = TRUE, text = "Dr. Eric Cabrera Estupinan",
            href = "http://www.htmlwidgets.org/") %>% 
hc_rangeSelector(selected = 4) %>%
hc_navigator( #outlineColor = "gray",
              outlineWidth = 2,
              series = list(color = "red",
                            lineWidth = 2,
                            type = "areaspline", # you can change the type
                            fillColor = "rgba(255, 0, 0, 0.2)"))#,   

})
```
 
### **CFR and CRR TS**

```{r}

renderHighchart({
  
country_main_sel<-input$si_count_main 
Main_count_data_cfr_crr<-data1 %>% filter(country==country_main_sel) %>%
  select(date, CFR, CRR)  
  
# set color palette
cols <- brewer.pal(7, "Set1")
#cols <- c("blue","green","red")

highchart (type="stock") %>%
  
  hc_add_series(data=Main_count_data_cfr_crr, 
                name="CFR",
                type="line", 
                hcaes(x=date, y=round(CFR, digits = 2))) %>% 
  hc_add_series(data=Main_count_data_cfr_crr,
                name="CRR",
                type="line", 
                hcaes(x=date, y=round(CRR, digits = 2))) %>%
hc_title(text=paste("Case Fatality Rate CFR and Case Recovered Rate CRR in", country_main_sel,"(Time Serie, TS)"),
         align="left",
         useHTML=TRUE) %>%
hc_subtitle(text="<i>Data source: https://github.com/CSSEGISandData/COVID-19/tree/master/csse_covid_19_data/csse_covid_19_time_series", 
            align="left",
            useHTML=TRUE) %>%   
hc_legend(enabled = TRUE) %>%
     hc_exporting(enabled = TRUE,
             filename="CFR_and_CRR_country_TS",
             formAttribute=list(target="_black"),
             buttons=list(contextButton=list(text="Export",
                                             theme=list(fill="transparent")))) %>%  # enable export
hc_colors(cols) %>%
hc_plotOptions(series = list(stacking = NULL,
                               marker = list(enabled = TRUE, symbol = "circle", size=1,
                                             states = list(hover = list(enabled = TRUE))),
                               lineWidth = 2,
                               fillColor="red")) %>%
hc_xAxis(title = list(text="time (days)"),
           type="datetime") %>%
hc_yAxis(title = list(text="CFR and CRR"),
           labels=list(format= "{value:,.0f}%"),
           opposite=FALSE) %>%
hc_tooltip(shared = FALSE,
             crosshairs=TRUE,
             bacgroundColor="transparent") %>% 
hc_credits(enabled = TRUE, text = "Dr. Eric Cabrera Estupinan",
            href = "http://www.htmlwidgets.org/") %>% 
hc_rangeSelector(selected = 4) %>%
hc_navigator( #outlineColor = "gray",
              outlineWidth = 2,
              series = list(color = "red",
                            lineWidth = 2,
                            type = "areaspline", # you can change the type
                            fillColor = "rgba(255, 0, 0, 0.2)"))#,   
})
```


Pick various countries {data-icon="fa-line-chart" data-orientation=columns data-navmenu="Countries"}
==========================================================================================

Column {.sidebar}
------------------------------------------------------------------
```{r select-input3}

 count_list_1<-data1 %>% select(country) %>% distinct(country)
 count_list_1<-as.character(count_list_1$country)
 
 selectInput(
   inputId = 'si_count1', label = ' Select Countries',
   choices = count_list_1, selected = "US", multiple = TRUE)

 dateInput(inputId = 'si_date2', 
          label = ' Select date (Only for radar chart)', 
          value = max_date,
          min = min_date, 
          max = max_date,
          format="yyyy-mm-dd")
```

```{r select-input7}

 selectInput(inputId = 'si_count2', label = 'Select Scale',
             choices = c("logarithmic", "linear"), 
             selected = "logarithmic", multiple = FALSE)
```


```{r select-input8}

 selectInput(inputId = 'si_count3', label = 'Radar Chart Type',
             choices = c("line", "area"), 
             selected = "line", multiple = FALSE)
```

Column {.tabset}
--------------------------------------------------------------------------------------

### **Confirmed cases TS**

```{r}

renderHighchart({

   countries_names<-input$si_count1

   data_main_count<- data1 %>%
     group_by(country) %>% 
     filter(country %in% c(countries_names)) %>% 
     select(country, date, total_cases, total_deaths, total_recovered, new_cases, new_deaths,
            new_recovered, CFR, CRR, factor1, factor2, factor3)
   
 # set color palette
cols <- brewer.pal(7, "Set1")
#cols <- c("blue","green","red")

highchart (type="stock") %>%

 hc_add_series(data=data_main_count,
#                name="CFR",
                type="line",
                hcaes(x=date, y=total_cases, group=country)) %>%
hc_title(text="Cumulative total confirmed: CASES, selected counties (Time Serie, TS)",
         align="left",
         useHTML=TRUE) %>%
hc_subtitle(text="<i>Data source: https://github.com/CSSEGISandData/COVID-19/tree/master/csse_covid_19_data/csse_covid_19_time_series",
            align="left",
            useHTML=TRUE) %>%
hc_legend(enabled = TRUE) %>%
hc_colors(cols) %>%
hc_plotOptions(series = list(stacking = NULL,
                               marker = list(enabled = TRUE, symbol = "circle", size=2,
                                             states = list(hover = list(enabled = TRUE))),
                               lineWidth = 2,
                               fillColor="red")) %>%
hc_xAxis(title = list(text="time (days)"),
           type="datetime") %>%
hc_yAxis(title = list(text="Confirmed cases"),
           labels=list(format= "{value:,.0f}"),
           opposite=FALSE) %>%
hc_tooltip(shared = FALSE,
             crosshairs=TRUE,
             bacgroundColor="transparent") %>%
hc_credits(enabled = TRUE, text = "Dr. Eric Cabrera Estupinan",
            href = "http://www.htmlwidgets.org/") %>% 
     hc_exporting(enabled = TRUE,
             filename="Confirmed_cases_various_countries",
             formAttribute=list(target="_black"),
             buttons=list(contextButton=list(text="Export",
                                             theme=list(fill="transparent")))) %>%  # enable export
hc_rangeSelector(selected = 4) %>%
hc_navigator( #outlineColor = "gray",
              outlineWidth = 2,
              series = list(color = "red",
                            lineWidth = 2,
                            type = "areaspline", # you can change the type
                            fillColor = "rgba(255, 0, 0, 0.2)"))#,   
})

```

### **Confirmed deaths TS**

```{r}

renderHighchart({

   countries_names<-input$si_count1
   data_main_count<- data1 %>%
     group_by(country) %>% 
     filter(country %in% c(countries_names)) %>% 
     select(country, date, total_cases, total_deaths, total_recovered, new_cases, new_deaths,
            new_recovered, CFR, CRR, factor1, factor2, factor3)
   
 # set color palette
cols <- brewer.pal(7, "Set1")
#cols <- c("blue","green","red")

highchart (type="stock") %>%

 hc_add_series(data=data_main_count,
#                name="CFR",
                type="line",
                hcaes(x=date, y=total_deaths, group=country)) %>%
hc_title(text="Cumulative total confirmed: DEATHS, selected counties (Time Serie, TS)",
         align="left",
         useHTML=TRUE) %>%
hc_subtitle(text="<i>Data source: https://github.com/CSSEGISandData/COVID-19/tree/master/csse_covid_19_data/csse_covid_19_time_series",
            align="left",
            useHTML=TRUE) %>%
hc_legend(enabled = TRUE) %>%
hc_colors(cols) %>%
hc_plotOptions(series = list(stacking = NULL,
                               marker = list(enabled = TRUE, symbol = "circle", size=2,
                                             states = list(hover = list(enabled = TRUE))),
                               lineWidth = 2,
                               fillColor="red")) %>%
hc_xAxis(title = list(text="time (days)"),
           type="datetime") %>%
hc_yAxis(title = list(text="Confirmed deaths"),
           labels=list(format= "{value:,.0f}"),
           opposite=FALSE) %>%
hc_tooltip(shared = FALSE,
             crosshairs=TRUE,
             bacgroundColor="transparent") %>%
hc_credits(enabled = TRUE, text = "Dr. Eric Cabrera Estupinan",
            href = "http://www.htmlwidgets.org/") %>% 
  hc_exporting(enabled = TRUE,
             filename="Confirmed_deaths_various_countries",
             formAttribute=list(target="_black"),
             buttons=list(contextButton=list(text="Export",
                                             theme=list(fill="transparent")))) %>%  # enable export
hc_rangeSelector(selected = 4) %>%
hc_navigator( #outlineColor = "gray",
              outlineWidth = 2,
              series = list(color = "red",
                            lineWidth = 2,
                            type = "areaspline", # you can change the type
                            fillColor = "rgba(255, 0, 0, 0.2)"))#,   
})

```

### **Confirmed recovered TS**

```{r}

renderHighchart({

   countries_names<-input$si_count1

   data_main_count<- data1 %>%
     group_by(country) %>% 
     filter(country %in% c(countries_names)) %>% 
     select(country, date, total_cases, total_deaths, total_recovered, new_cases, new_deaths,
            new_recovered, CFR, CRR, factor1, factor2, factor3)
   
 # set color palette
cols <- brewer.pal(7, "Set1")
#cols <- c("blue","green","red")

highchart (type="stock") %>%

 hc_add_series(data=data_main_count,
#                name="CFR",
                type="line",
                hcaes(x=date, y=total_recovered, group=country)) %>%
hc_title(text="Cumulative total confirmed: RECOVERED, selected counties (Time Serie, TS)",
         align="left",
         useHTML=TRUE) %>%
hc_subtitle(text="<i>Data source: https://github.com/CSSEGISandData/COVID-19/tree/master/csse_covid_19_data/csse_covid_19_time_series",
            align="left",
            useHTML=TRUE) %>%
hc_legend(enabled = TRUE) %>%
hc_colors(cols) %>%
hc_plotOptions(series = list(stacking = NULL,
                               marker = list(enabled = TRUE, symbol = "circle", size=2,
                                             states = list(hover = list(enabled = TRUE))),
                               lineWidth = 2,
                               fillColor="red")) %>%
hc_xAxis(title = list(text="time (days)"),
           type="datetime") %>%
hc_yAxis(title = list(text="Confirmed recovered"),
           labels=list(format= "{value:,.0f}"),
           opposite=FALSE) %>%
hc_tooltip(shared = FALSE,
             crosshairs=TRUE,
             bacgroundColor="transparent") %>%
hc_credits(enabled = TRUE, text = "Dr. Eric Cabrera Estupinan",
            href = "http://www.htmlwidgets.org/") %>% 
  hc_exporting(enabled = TRUE,
             filename="Confirmed_recovered_various_countries",
             formAttribute=list(target="_black"),
             buttons=list(contextButton=list(text="Export",
                                             theme=list(fill="transparent")))) %>%  # enable export
hc_rangeSelector(selected = 4) %>%
hc_navigator( #outlineColor = "gray",
              outlineWidth = 2,
              series = list(color = "red",
                            lineWidth = 2,
                            type = "areaspline", # you can change the type
                            fillColor = "rgba(255, 0, 0, 0.2)"))#,   
})

```

### **New cases TS**

```{r}

renderHighchart({

   countries_names<-input$si_count1

   data_main_count<- data1 %>%
     group_by(country) %>% 
     filter(country %in% c(countries_names)) %>% 
     select(country, date, total_cases, total_deaths, total_recovered, new_cases, new_deaths,
            new_recovered, CFR, CRR, factor1, factor2, factor3)
   
 # set color palette
cols <- brewer.pal(7, "Set1")
#cols <- c("blue","green","red")

highchart (type="stock") %>%

hc_add_series(data=data_main_count,
#                name="CFR",
                type="line",
                hcaes(x=date, y=new_cases, group=country)) %>%
hc_title(text="New confirmed: CASES, selected counties (Time Serie, TS)",
         align="left",
         useHTML=TRUE) %>%
hc_subtitle(text="<i>Data source: https://github.com/CSSEGISandData/COVID-19/tree/master/csse_covid_19_data/csse_covid_19_time_series",
            align="left",
            useHTML=TRUE) %>%
hc_legend(enabled = TRUE) %>%
hc_colors(cols) %>%
hc_plotOptions(series = list(stacking = NULL,
                               marker = list(enabled = TRUE, symbol = "circle", size=2,
                                             states = list(hover = list(enabled = TRUE))),
                               lineWidth = 2,
                               fillColor="red")) %>%
hc_xAxis(title = list(text="time (days)"),
           type="datetime") %>%
hc_yAxis(title = list(text="Confirmed new cases"),
           labels=list(format= "{value:,.0f}"),
           opposite=FALSE) %>%
hc_tooltip(shared = FALSE,
             crosshairs=TRUE,
             bacgroundColor="transparent") %>%
hc_credits(enabled = TRUE, text = "Dr. Eric Cabrera Estupinan",
            href = "http://www.htmlwidgets.org/") %>% 
  hc_exporting(enabled = TRUE,
             filename="Confirmed_Daily_cases_various_countries",
             formAttribute=list(target="_black"),
             buttons=list(contextButton=list(text="Export",
                                             theme=list(fill="transparent")))) %>%  # enable export
hc_rangeSelector(selected = 4) %>%
hc_navigator( #outlineColor = "gray",
              outlineWidth = 2,
              series = list(color = "red",
                            lineWidth = 2,
                            type = "areaspline", # you can change the type
                            fillColor = "rgba(255, 0, 0, 0.2)"))#,   
})

```

### **New deaths TS**

```{r}

renderHighchart({

   countries_names<-input$si_count1

   data_main_count<- data1 %>%
     group_by(country) %>% 
     filter(country %in% c(countries_names)) %>% 
     select(country, date, total_cases, total_deaths, total_recovered, new_cases, new_deaths,
            new_recovered, CFR, CRR, factor1, factor2, factor3)
   
 # set color palette
cols <- brewer.pal(7, "Set1")
#cols <- c("blue","green","red")

highchart (type="stock") %>%

 hc_add_series(data=data_main_count,
#                name="CFR",
                type="line",
                hcaes(x=date, y=new_deaths, group=country)) %>%
hc_title(text="New confirmed: DEATHS, selected counties (Time Serie, TS)",
         align="left",
         useHTML=TRUE) %>%
hc_subtitle(text="<i>Data source: https://github.com/CSSEGISandData/COVID-19/tree/master/csse_covid_19_data/csse_covid_19_time_series",
            align="left",
            useHTML=TRUE) %>%
hc_legend(enabled = TRUE) %>%
hc_colors(cols) %>%
hc_plotOptions(series = list(stacking = NULL,
                               marker = list(enabled = TRUE, symbol = "circle", size=2,
                                             states = list(hover = list(enabled = TRUE))),
                               lineWidth = 2,
                               fillColor="red")) %>%
hc_xAxis(title = list(text="time (days)"),
           type="datetime") %>%
hc_yAxis(title = list(text="Confirmed new deaths"),
           labels=list(format= "{value:,.0f}"),
           opposite=FALSE) %>%
hc_tooltip(shared = FALSE,
             crosshairs=TRUE,
             bacgroundColor="transparent") %>%
hc_credits(enabled = TRUE, text = "Dr. Eric Cabrera Estupinan",
            href = "http://www.htmlwidgets.org/") %>% 
    hc_exporting(enabled = TRUE,
             filename="Confirmed_Daily_deaths_various_countries",
             formAttribute=list(target="_black"),
             buttons=list(contextButton=list(text="Export",
                                             theme=list(fill="transparent")))) %>%  # enable export
hc_rangeSelector(selected = 4) %>%
hc_navigator( #outlineColor = "gray",
              outlineWidth = 2,
              series = list(color = "red",
                            lineWidth = 2,
                            type = "areaspline", # you can change the type
                            fillColor = "rgba(255, 0, 0, 0.2)"))#,   
})
```

### **New recovered TS**

```{r}

renderHighchart({

   countries_names<-input$si_count1

   data_main_count<- data1 %>%
     group_by(country) %>% 
     filter(country %in% c(countries_names)) %>% 
     select(country, date, total_cases, total_deaths, total_recovered, new_cases, new_deaths,
            new_recovered, CFR, CRR, factor1, factor2, factor3)
   
 # set color palette
cols <- brewer.pal(7, "Set1")
#cols <- c("blue","green","red")

highchart (type="stock") %>%

 hc_add_series(data=data_main_count,
#                name="CFR",
                type="line",
                hcaes(x=date, y=new_recovered, group=country)) %>%
hc_title(text="New confirmed: RECOVERED, selected counties (Time Serie, TS)",
         align="left",
         useHTML=TRUE) %>%
hc_subtitle(text="<i>Data source: https://github.com/CSSEGISandData/COVID-19/tree/master/csse_covid_19_data/csse_covid_19_time_series",
            align="left",
            useHTML=TRUE) %>%
hc_legend(enabled = TRUE) %>%
hc_colors(cols) %>%
hc_plotOptions(series = list(stacking = NULL,
                               marker = list(enabled = TRUE, symbol = "circle", size=2,
                                             states = list(hover = list(enabled = TRUE))),
                               lineWidth = 2,
                               fillColor="red")) %>%
hc_xAxis(title = list(text="time (days)"),
           type="datetime") %>%
hc_yAxis(title = list(text="Confirmed new recovered"),
           labels=list(format= "{value:,.0f}"),
           opposite=FALSE) %>%
hc_tooltip(shared = FALSE,
             crosshairs=TRUE,
             bacgroundColor="transparent") %>%
hc_credits(enabled = TRUE, text = "Dr. Eric Cabrera Estupinan",
            href = "http://www.htmlwidgets.org/") %>% 
  hc_exporting(enabled = TRUE,
             filename="Confirmed_Daily_recovered_various_countries",
             formAttribute=list(target="_black"),
             buttons=list(contextButton=list(text="Export",
                                             theme=list(fill="transparent")))) %>%  # enable export
hc_rangeSelector(selected = 4) %>%
hc_navigator( #outlineColor = "gray",
              outlineWidth = 2,
              series = list(color = "red",
                            lineWidth = 2,
                            type = "areaspline", # you can change the type
                            fillColor = "rgba(255, 0, 0, 0.2)"))#,   
})

```

### **CFR TS**

```{r}

renderHighchart({

   countries_names<-input$si_count1

   data_main_count<- data1 %>%
     group_by(country) %>% 
     filter(country %in% c(countries_names)) %>% 
     select(country, date, total_cases, total_deaths, total_recovered, new_cases, new_deaths,
            new_recovered, CFR, CRR, factor1, factor2, factor3)
   
 # set color palette
cols <- brewer.pal(7, "Set1")
#cols <- c("blue","green","red")

highchart (type="stock") %>%

 hc_add_series(data=data_main_count,
#                name="CFR",
                type="line",
                hcaes(x=date, y=CFR, group=country)) %>%
hc_title(text="Case fatality rate CFR, selected counties (Time Serie, TS)",
         align="left",
         useHTML=TRUE) %>%
hc_subtitle(text="<i>Data source: https://github.com/CSSEGISandData/COVID-19/tree/master/csse_covid_19_data/csse_covid_19_time_series",
            align="left",
            useHTML=TRUE) %>%
hc_legend(enabled = TRUE) %>%
hc_colors(cols) %>%
hc_plotOptions(series = list(stacking = NULL,
                               marker = list(enabled = TRUE, symbol = "circle", size=2,
                                             states = list(hover = list(enabled = TRUE))),
                               lineWidth = 2,
                               fillColor="red")) %>%
hc_xAxis(title = list(text="time (days)"),
           type="datetime") %>%
hc_yAxis(title = list(text="CFR"),
           labels=list(format= "{value:,.0f}%"),
           opposite=FALSE) %>%
hc_tooltip(shared = FALSE,
             crosshairs=TRUE,
             bacgroundColor="transparent") %>%
hc_credits(enabled = TRUE, text = "Dr. Eric Cabrera Estupinan",
            href = "http://www.htmlwidgets.org/") %>% 
      hc_exporting(enabled = TRUE,
             filename="CFR_various_countries",
             formAttribute=list(target="_black"),
             buttons=list(contextButton=list(text="Export",
                                             theme=list(fill="transparent")))) %>%  # enable export
hc_rangeSelector(selected = 4) %>%
hc_navigator( #outlineColor = "gray",
              outlineWidth = 2,
              series = list(color = "red",
                            lineWidth = 2,
                            type = "areaspline", # you can change the type
                            fillColor = "rgba(255, 0, 0, 0.2)"))#,   
})

```

### **CRR TS**

```{r}

renderHighchart({

   countries_names<-input$si_count1

   data_main_count<- data1 %>%
     group_by(country) %>% 
     filter(country %in% c(countries_names)) %>% 
     select(country, date, total_cases, total_deaths, total_recovered, new_cases, new_deaths,
            new_recovered, CFR, CRR, factor1, factor2, factor3)
   
 # set color palette
cols <- brewer.pal(7, "Set1")
#cols <- c("blue","green","red")

highchart (type="stock") %>%

 hc_add_series(data=data_main_count,
#                name="CFR",
                type="line",
                hcaes(x=date, y=CRR, group=country)) %>%
hc_title(text="Case recovered rate CRR, selected counties (Time Serie, TS)",
         align="left",
         useHTML=TRUE) %>%
hc_subtitle(text="<i>Data source: https://github.com/CSSEGISandData/COVID-19/tree/master/csse_covid_19_data/csse_covid_19_time_series",
            align="left",
            useHTML=TRUE) %>%
hc_legend(enabled = TRUE) %>%
hc_colors(cols) %>%
hc_plotOptions(series = list(stacking = NULL,
                               marker = list(enabled = TRUE, symbol = "circle", size=2,
                                             states = list(hover = list(enabled = TRUE))),
                               lineWidth = 2,
                               fillColor="red")) %>%
hc_xAxis(title = list(text="time (days)"),
           type="datetime") %>%
hc_yAxis(title = list(text="CRR"),
           labels=list(format= "{value:,.0f}%"),
           opposite=FALSE) %>%
hc_tooltip(shared = FALSE,
             crosshairs=TRUE,
             bacgroundColor="transparent") %>%
hc_credits(enabled = TRUE, text = "Dr. Eric Cabrera Estupinan",
            href = "http://www.htmlwidgets.org/") %>% 
hc_exporting(enabled = TRUE,
             filename="CRR_various_countries",
             formAttribute=list(target="_black"),
             buttons=list(contextButton=list(text="Export",
                                             theme=list(fill="transparent")))) %>%  # enable export
hc_rangeSelector(selected = 4) %>%
hc_navigator( #outlineColor = "gray",
              outlineWidth = 2,
              series = list(color = "red",
                            lineWidth = 2,
                            type = "areaspline", # you can change the type
                            fillColor = "rgba(255, 0, 0, 0.2)"))#,   
})

```

### **Cases per 100000 inhab TS**

```{r}

renderHighchart({

   countries_names<-input$si_count1

   data_main_count<- data1 %>%
     group_by(country) %>% 
     filter(country %in% c(countries_names)) %>% 
     select(country, date, total_cases, total_deaths, total_recovered, new_cases, new_deaths,
            new_recovered, CFR, CRR, factor1, factor2, factor3)
   
 # set color palette
cols <- brewer.pal(7, "Set1")
#cols <- c("blue","green","red")

highchart (type="stock") %>%

 hc_add_series(data=data_main_count,
#                name="CFR",
                type="line",
                hcaes(x=date, y=factor1, group=country)) %>%
hc_title(text="Cases per 100000 inhabitant, selected counties (Time Serie, TS)",
         align="left",
         useHTML=TRUE) %>%
hc_subtitle(text="<i>Data source: https://github.com/CSSEGISandData/COVID-19/tree/master/csse_covid_19_data/csse_covid_19_time_series",
            align="left",
            useHTML=TRUE) %>%
hc_legend(enabled = TRUE) %>%
hc_colors(cols) %>%
hc_plotOptions(series = list(stacking = NULL,
                               marker = list(enabled = TRUE, symbol = "circle", size=2,
                                             states = list(hover = list(enabled = TRUE))),
                               lineWidth = 2,
                               fillColor="red")) %>%
hc_xAxis(title = list(text="time (days)"),
           type="datetime") %>%
hc_yAxis(title = list(text="Cases per 100000 inhab"),
           labels=list(format= "{value:,.0f}"),
           opposite=FALSE) %>%
hc_tooltip(shared = FALSE,
             crosshairs=TRUE,
             bacgroundColor="transparent") %>%
hc_credits(enabled = TRUE, text = "Dr. Eric Cabrera Estupinan",
            href = "http://www.htmlwidgets.org/") %>% 
hc_exporting(enabled = TRUE,
             filename="Cases_per_hundredthousand_countries",
             formAttribute=list(target="_black"),
             buttons=list(contextButton=list(text="Export",
                                             theme=list(fill="transparent")))) %>%  # enable export
hc_rangeSelector(selected = 4) %>%
hc_navigator( #outlineColor = "gray",
              outlineWidth = 2,
              series = list(color = "red",
                            lineWidth = 2,
                            type = "areaspline", # you can change the type
                            fillColor = "rgba(255, 0, 0, 0.2)"))#,   
})

```

### **Deaths per 100000 inhab TS**

```{r}

renderHighchart({

   countries_names<-input$si_count1

   data_main_count<- data1 %>%
     group_by(country) %>% 
     filter(country %in% c(countries_names)) %>% 
     select(country, date, total_cases, total_deaths, total_recovered, new_cases, new_deaths,
            new_recovered, CFR, CRR, factor1, factor2, factor3)
   
 # set color palette
cols <- brewer.pal(7, "Set1")
#cols <- c("blue","green","red")

highchart (type="stock") %>%

 hc_add_series(data=data_main_count,
#                name="CFR",
                type="line",
                hcaes(x=date, y=factor2, group=country)) %>%
hc_title(text="Deaths per 100000 inhabitant, selected counties (Time Serie, TS)",
         align="left",
         useHTML=TRUE) %>%
hc_subtitle(text="<i>Data source: https://github.com/CSSEGISandData/COVID-19/tree/master/csse_covid_19_data/csse_covid_19_time_series",
            align="left",
            useHTML=TRUE) %>%
hc_legend(enabled = TRUE) %>%
hc_colors(cols) %>%
hc_plotOptions(series = list(stacking = NULL,
                               marker = list(enabled = TRUE, symbol = "circle", size=2,
                                             states = list(hover = list(enabled = TRUE))),
                               lineWidth = 2,
                               fillColor="red")) %>%
hc_xAxis(title = list(text="time (days)"),
           type="datetime") %>%
hc_yAxis(title = list(text="Deaths per 100000 inhab"),
           labels=list(format= "{value:,.0f}"),
           opposite=FALSE) %>%
hc_tooltip(shared = FALSE,
             crosshairs=TRUE,
             bacgroundColor="transparent") %>%
hc_credits(enabled = TRUE, text = "Dr. Eric Cabrera Estupinan",
            href = "http://www.htmlwidgets.org/") %>% 
  hc_exporting(enabled = TRUE,
             filename="Deaths_per_hundredthousand_countries",
             formAttribute=list(target="_black"),
             buttons=list(contextButton=list(text="Export",
                                             theme=list(fill="transparent")))) %>%  # enable export
hc_rangeSelector(selected = 4) %>%
hc_navigator( #outlineColor = "gray",
              outlineWidth = 2,
              series = list(color = "red",
                            lineWidth = 2,
                            type = "areaspline", # you can change the type
                            fillColor = "rgba(255, 0, 0, 0.2)"))#,   
})
```

### **Recovered per 100000 inhab TS**

```{r}

renderHighchart({

   countries_names<-input$si_count1

   data_main_count<- data1 %>%
     group_by(country) %>% 
     filter(country %in% c(countries_names)) %>% 
     select(country, date, total_cases, total_deaths, total_recovered, new_cases, new_deaths,
            new_recovered, CFR, CRR, factor1, factor2, factor3)
   
 # set color palette
cols <- brewer.pal(7, "Set1")
#cols <- c("blue","green","red")

highchart (type="stock") %>%

 hc_add_series(data=data_main_count,
#                name="CFR",
                type="line",
                hcaes(x=date, y=factor3, group=country)) %>%
hc_title(text="Recovered per 100000 inhabitant, selected counties (Time Serie, TS)",
         align="left",
         useHTML=TRUE) %>%
hc_subtitle(text="<i>Data source: https://github.com/CSSEGISandData/COVID-19/tree/master/csse_covid_19_data/csse_covid_19_time_series",
            align="left",
            useHTML=TRUE) %>%
hc_legend(enabled = TRUE) %>%
hc_colors(cols) %>%
hc_plotOptions(series = list(stacking = NULL,
                               marker = list(enabled = TRUE, symbol = "circle", size=2,
                                             states = list(hover = list(enabled = TRUE))),
                               lineWidth = 2,
                               fillColor="red")) %>%
hc_xAxis(title = list(text="time (days)"),
           type="datetime") %>%
hc_yAxis(title = list(text="Recovered per 100000 inhab"),
           labels=list(format= "{value:,.0f}"),
           opposite=FALSE) %>%
hc_tooltip(shared = FALSE,
             crosshairs=TRUE,
             bacgroundColor="transparent") %>%
hc_credits(enabled = TRUE, text = "Dr. Eric Cabrera Estupinan",
            href = "http://www.htmlwidgets.org/") %>% 
hc_exporting(enabled = TRUE,
             filename="Recovered_per_hundredthousand_countries",
             formAttribute=list(target="_black"),
             buttons=list(contextButton=list(text="Export",
                                             theme=list(fill="transparent")))) %>%  # enable export
hc_rangeSelector(selected = 4) %>%
hc_navigator( #outlineColor = "gray",
              outlineWidth = 2,
              series = list(color = "red",
                            lineWidth = 2,
                            type = "areaspline", # you can change the type
                            fillColor = "rgba(255, 0, 0, 0.2)"))#,   
})
```

### **Cases vs new cases TS**

```{r}
renderHighchart({

countries_names<-input$si_count1
#countries_names<-c("Cuba","Argentina")

scale_name<-input$si_count2

 data_confront<- data1 %>%
   filter(country %in% c(countries_names)) %>% 
   filter(total_cases!=0) %>% 
   select(country, date, total_cases, new_cases) 
 #data_confront<-rename(data_confront, 'Total_cases ' = 'total_cases', 'New_daily_cases' = 'new_cases')

 cols<- brewer.pal(7, "Set1")
 
 hchart(data_confront, type="line", hcaes(x=total_cases, y= new_cases, group=country),
        showInLegend=TRUE, xLab="Total cases") %>% 
 hc_colors(cols) %>% 
 hc_title(text= "Total cumulative cases vs New daily cases in the selected countries", 
          align="left",
          useHTML=TRUE) %>% 
 hc_subtitle(text="<i>Data source: https://github.com/CSSEGISandData/COVID-19/tree/master/csse_covid_19_data/csse_covid_19_time_series", 
          align="left",
          useHTML=TRUE) %>%
 hc_legend(enabled = TRUE) %>%
   hc_exporting(enabled = TRUE,
             filename="Cases_vs_DailyCases_countries",
             formAttribute=list(target="_black"),
             buttons=list(contextButton=list(text="Export",
                                             theme=list(fill="transparent")))) %>%  # enable export
 hc_xAxis(type= (scale_name), tickInterval= 1, gridLineWidth= 1, minorTickInterval= 0.1,
          labels=list(format= "{value:,.0f}"), title = list(text="Total cumulative cases")) %>% 
 hc_yAxis(type= (scale_name), tickInterval= 1, gridLineWidth= 1, minorTickInterval= 0.1,
          labels=list(format= "{value:,.0f}"), title = list(text="New daily cases")) %>% 
   hc_plotOptions(series = list(stacking = NULL,
                               marker = list(enabled = TRUE, symbol = "circle", size=1,
                                             states = list(hover = list(enabled = TRUE))),
                               lineWidth = 1,
                               fillColor="red")) %>%
#hc_chart(style = list(fontFamily = "Georgia",
#                      fontWeight = "bold")) %>% 
  hc_tooltip(borderWidth = 2,
            bacgroundColor="transparent", 
            pointFormat = "Country: {point.country} <br> Date: {point.date} <br> Total cases: {point.total_cases:.0f} <br> New daily cases: {point.new_cases:.0f}") %>%
  hc_credits(enabled = TRUE, text = "Dr. Eric Cabrera Estupinan",
           href = "http://www.htmlwidgets.org/") 
})

```

### **Radar**

```{r}

renderHighchart({

select_count_date<-input$si_date2
#select_count_date<-curr_date

countries_names<-input$si_count1
#countries_names<-c("Cuba","Argentina")

radar_type<-input$si_count3

 data_radar<- data1 %>%
   filter(date==select_count_date) %>% 
   filter(country %in% c(countries_names)) %>% 
   select(country, date, CFR, CRR, factor1, factor2, factor3)  

 data_radar[,6]<-round(data_radar[,6]*10, digits=2) #Cambio a muertos por cada millon
 data_radar[,3]<-round(data_radar[,3]*10, digits=2) #Cambio a CFR *1000, es decir (Tot_deaths/Tot_cases)*1000
 
# data_radar %>% 
   data_radar<- rename(data_radar, 'Case fatality rate CFR= (Tot_deaths/Tot_cases)*1000' = 'CFR', 'Case recovered rate CRR (%)'='CRR',
                       'Cases per 100000 Inhabitant'='factor1','Deaths per million Inhabitant'='factor2',
                       'Recovered per 100000 Inhabitant'='factor3')
          
 gather_radar_data<-gather(data_radar, "Variables", "n", 3:7) 
 gather_radar_data[,4]<-round(gather_radar_data[,4], digits=2)
 
 
 
 cols<- brewer.pal(7, "Set1")
 
 hchart(gather_radar_data, type=(radar_type), hcaes(x=Variables, y=n , group=country), showInLegend=TRUE) %>%
   hc_chart(polar = TRUE) %>%
 hc_colors(cols) %>% 
 hc_title(text= paste("Main variables behavior, country comparison. Date:", select_count_date), 
          align="left",
          useHTML=TRUE) %>% 
 hc_subtitle(text="<i>Data source: https://github.com/CSSEGISandData/COVID-19/tree/master/csse_covid_19_data/csse_covid_19_time_series", 
          align="left",
          useHTML=TRUE) %>%
 hc_legend(enabled = TRUE) %>% 
   hc_exporting(enabled = TRUE,
             filename="radar_countries",
             formAttribute=list(target="_black"),
             buttons=list(contextButton=list(text="Export",
                                             theme=list(fill="transparent")))) %>%  # enable export
#hc_chart(style = list(fontFamily = "Georgia",
#                      fontWeight = "bold")) %>% 
 hc_tooltip(borderWidth = 2,
           bacgroundColor="transparent") %>% 
#           pointFormat = "{point.casos}: {point.tot_cas:.0f}<br> {point.porciento}: {point.percent:.2f}%") %>% 
 hc_credits(enabled = TRUE, text = "Dr. Eric Cabrera Estupinan",
           href = "http://www.htmlwidgets.org/")
})

```

Top 10 countries {data-icon="fa-line-chart" data-orientation=columns data-navmenu="Countries"}
==========================================================================================

Column {.sidebar}
------------------------------------------------------------------
```{r select-input16}

dateInput(inputId = 'si_3', 
          label = ' Select date', 
          value = max_date,
          min = min_date, 
          max = max_date,
          format="yyyy-mm-dd")
```

```{r select-input14}

 selectInput(inputId = 'si_count9', label = 'Select variable',
             choices = c("Total Confirmed Cases", "Total Confirmed Deaths", "Total Confirmed Recovered",
                         "Case Fatality Rate CFR","Case Recovered Rate CRR", "Cases per 100000 inhab",
                         "Deaths per 100000 inhab", "Recovered per 100000 inhab"), 
             selected = "Total Confirmed Cases", multiple = FALSE)
```

```{r select-input15}

 list_var<-c("treemap", "sunburst")
 
 selectInput(
   inputId = 'si_var_ts1', label = 'Select chart type',
   choices = c(list_var), selected = "treemap", multiple = FALSE)
```

```{r select-input17}

 selectInput(inputId = 'si_count10', label = 'Select Scale',
             choices = c("logarithmic", "linear"), 
             selected = "logarithmic", multiple = FALSE)
```

Column {.tabset}
--------------------------------------------------------------------------------------

### **Treemap & sunburst**

```{r, fig.keep='none'}

renderHighchart({

date_for_chart<-input$si_3
#date_for_chart<-curr_date

chart_type<-input$si_var_ts1
#chart_type<-c("treemap")

Variab<-input$si_count9
#Variab<-c("Total Confirmed Cases")

Country_chart_data<- data1 %>%    #All countries with date selected
  filter(date==date_for_chart)

 if (Variab=="Total Confirmed Cases"){
       varsize<-"total_cases"
       Top_10_count_df<- Country_chart_data[order(Country_chart_data$total_cases,decreasing = T)[1:10],]
 } else {}
 if (Variab=="Total Confirmed Deaths"){
       varsize<-"total_deaths"
       Top_10_count_df<- Country_chart_data[order(Country_chart_data$total_deaths,decreasing = T)[1:10],]
 } else {}
 if (Variab=="Total Confirmed Recovered"){
       varsize<-"total_recovered"
       Top_10_count_df<- Country_chart_data[order(Country_chart_data$total_recovered,decreasing = T)[1:10],]
 } else {}
 if (Variab=="Case Fatality Rate CFR"){
       varsize<-"CFR"
       Top_10_count_df<- Country_chart_data[order(Country_chart_data$CFR,decreasing = T)[1:10],]
 } else {}
if (Variab=="Case Recovered Rate CRR"){
       varsize<-"CRR"
       Top_10_count_df<- Country_chart_data[order(Country_chart_data$CRR,decreasing = T)[1:10],]
 } else {}
if (Variab=="Cases per 100000 inhab"){
       varsize<-"factor1"
       Top_10_count_df<- Country_chart_data[order(Country_chart_data$factor1,decreasing = T)[1:10],]
 } else {}
if (Variab=="Deaths per 100000 inhab"){
       varsize<-"factor2"
       Top_10_count_df<- Country_chart_data[order(Country_chart_data$factor2,decreasing = T)[1:10],]
 } else {}
if (Variab=="Recovered per 100000 inhab"){
       varsize<-"factor3"
       Top_10_count_df<- Country_chart_data[order(Country_chart_data$factor3,decreasing = T)[1:10],]
 } else {}

tm1<- data_to_hierarchical(data=Top_10_count_df,
                     group_vars = c("region","country"),
                     size_var = c(varsize),
                     colors = getOption("highcharter.color_palette"))

hchart(tm1, type = chart_type) %>% 
hc_title(text= paste("Top 10", Variab, "by countries and Regions. Date:", date_for_chart), 
           align="left",
           useHTML=TRUE) %>% 
 hc_subtitle(text="<i>Data source: https://github.com/CSSEGISandData/COVID-19/tree/master/csse_covid_19_data/csse_covid_19_time_series", 
           align="left",
           useHTML=TRUE) %>%
 hc_legend(enabled = TRUE) %>% 
 hc_exporting(enabled = TRUE,
             filename="Top_ten_variables",
             formAttribute=list(target="_black"),
             buttons=list(contextButton=list(text="Export",
                                             theme=list(fill="transparent")))) %>%  # enable export
hc_credits(enabled = TRUE, text = "Dr. Eric Cabrera Estupinan",
           href = "http://www.htmlwidgets.org/")
})

```

### **Bar plot**

```{r}

renderHighchart({

date_for_chart<-input$si_3
#date_for_chart<-curr_date

Variab<-input$si_count9
#Variab<-c("Total Confirmed Cases")


Country_chart_data<- data1 %>%    #All countries with date selected
  filter(date==date_for_chart)

 if (Variab=="Total Confirmed Cases"){
       col_obj<-Country_chart_data$total_cases
 } else {}
 if (Variab=="Total Confirmed Deaths"){
       col_obj<-Country_chart_data$total_deaths   
 } else {}
 if (Variab=="Total Confirmed Recovered"){
       col_obj<-Country_chart_data$total_recovered 
 } else {}
 if (Variab=="Case Fatality Rate CFR"){
       col_obj<-Country_chart_data$CFR
 } else {}
if (Variab=="Case Recovered Rate CRR"){
       col_obj<- Country_chart_data$CRR
 } else {}
if (Variab=="Cases per 100000 inhab"){
       col_obj<- Country_chart_data$factor1
 } else {}
if (Variab=="Deaths per 100000 inhab"){
       col_obj<- Country_chart_data$factor2
 } else {}
if (Variab=="Recovered per 100000 inhab"){
       col_obj<- Country_chart_data$factor3
 } else {}

Country_chart_data<-cbind(Country_chart_data,col_obj)

Top_10_count_df<- Country_chart_data[order(Country_chart_data$col_obj,decreasing = T)[1:10],]

hchart(Top_10_count_df, 
       type = "bar", 
       hcaes(x=country, y=col_obj),
       name="Top 10 Countries",
       showInLegend = TRUE) %>% 
hc_colors(getOption("highcharter.color_palette")) %>% 
hc_legend(enabled = TRUE) %>%  
hc_yAxis(title = list(text=paste0(Variab))) %>% 
hc_xAxis(title = list(text="Countries")) %>%
hc_title(text= paste("Top 10", Variab, "by countries and Regions. Date:", date_for_chart), 
           align="left",
           useHTML=TRUE) %>% 
 hc_subtitle(text="<i>Data source: https://github.com/CSSEGISandData/COVID-19/tree/master/csse_covid_19_data/csse_covid_19_time_series", 
           align="left",
           useHTML=TRUE) %>%
 hc_legend(enabled = TRUE) %>% 
  hc_exporting(enabled = TRUE,
             filename="Top_ten_variables_barplot",
             formAttribute=list(target="_black"),
             buttons=list(contextButton=list(text="Export",
                                             theme=list(fill="transparent")))) %>%  # enable export
hc_credits(enabled = TRUE, text = "Dr. Eric Cabrera Estupinan",
           href = "http://www.htmlwidgets.org/") 
})
```


Column {.tabset}
--------------------------------------

### **Top 10 countries TS**
```{r}

renderHighchart({

date_for_chart<-input$si_3
#date_for_chart<-curr_date

Variab<-input$si_count9
#Variab<-c("Total Confirmed Cases") 

var_scale<-input$si_count10
#var_scale<-c("logarithmic")
  
Country_chart_data<- data1 %>%    #All countries with date selected
  filter(date==date_for_chart)  
  
if (Variab=="Total Confirmed Cases"){
       col_obj<-Country_chart_data$total_cases
 } else {}
 if (Variab=="Total Confirmed Deaths"){
       col_obj<-Country_chart_data$total_deaths   
 } else {}
 if (Variab=="Total Confirmed Recovered"){
       col_obj<-Country_chart_data$total_recovered 
 } else {}
 if (Variab=="Case Fatality Rate CFR"){
       col_obj<-Country_chart_data$CFR
 } else {}
if (Variab=="Case Recovered Rate CRR"){
       col_obj<- Country_chart_data$CRR
 } else {}
if (Variab=="Cases per 100000 inhab"){
       col_obj<- Country_chart_data$factor1
 } else {}
if (Variab=="Deaths per 100000 inhab"){
       col_obj<- Country_chart_data$factor2
 } else {}
if (Variab=="Recovered per 100000 inhab"){
       col_obj<- Country_chart_data$factor3
 } else {}

Country_chart_data<-cbind(Country_chart_data,col_obj)

Top_10_count_df<- Country_chart_data[order(Country_chart_data$col_obj,decreasing = T)[1:10],]  
top_10_count_name<-Top_10_count_df$country

data_main_count<- data1 %>%
     group_by(country) %>% 
     filter(country %in% c(top_10_count_name)) %>% 
     select(country, date, total_cases, total_deaths, total_recovered, new_cases, new_deaths,
            new_recovered, CFR, CRR, factor1, factor2, factor3) %>% 
ungroup()

if (Variab=="Total Confirmed Cases"){
       col_obj1<-data_main_count$total_cases
       auxvect<-as.data.frame(col_obj1)
} else {}
if (Variab=="Total Confirmed Deaths"){
       col_obj1<-data_main_count$total_deaths
       auxvect<-as.data.frame(col_obj1)
} else {}
if (Variab=="Total Confirmed Recovered"){
       col_obj1<-data_main_count$total_recovered
       auxvect<-as.data.frame(col_obj1)
} else {}
if (Variab=="Case Fatality Rate CFR"){
       col_obj1<-data_main_count$CFR
       auxvect<-as.data.frame(col_obj1)
} else {}
if (Variab=="Case Recovered Rate CRR"){
       col_obj1<-data_main_count$CRR
       auxvect<-as.data.frame(col_obj1)
} else {}
if (Variab=="Cases per 100000 inhab"){
       col_obj1<-data_main_count$factor1
       auxvect<-as.data.frame(col_obj1)
 } else {}
if (Variab=="Deaths per 100000 inhab"){
       col_obj1<-data_main_count$factor2
       auxvect<-as.data.frame(col_obj1)
 } else {}
if (Variab=="Recovered per 100000 inhab"){
       col_obj1<-data_main_count$factor3
       auxvect<-as.data.frame(col_obj1)
 } else {}

data_main_count<-cbind(data_main_count,auxvect)

vect_min_date<-data_main_count %>%      #vector of all the min dates for each country
  group_by(country) %>%
  summarise(min_date=min(date))
date_min<-max(vect_min_date$min_date)    #max date of all min dates of the selected countries

date_for_chart1<-as.Date(date_for_chart)

data_main_count<-data_main_count %>%    #data frame with "top 10 countries TS" between lower and upper dates.
  group_by(country) %>% 
  filter(between(date, date_min, date_for_chart1))

cols <- brewer.pal(7, "Set1")

highchart (type="stock") %>%

hc_add_series(data=data_main_count,
#                name="CFR",
                type="line",
                hcaes(x=date, y=col_obj1, group=country)) %>%
hc_title(text=paste("Top 10", Variab, "by countries. Date:", date_for_chart, "(Time Serie, TS)"),
         align="left",
         useHTML=TRUE) %>%
hc_subtitle(text="<i>Data source: https://github.com/CSSEGISandData/COVID-19/tree/master/csse_covid_19_data/csse_covid_19_time_series",
            align="left",
            useHTML=TRUE) %>%
hc_legend(enabled = TRUE) %>%
hc_colors(cols) %>%
hc_xAxis(title = list(text="time (days)"),
           type="datetime") %>%
hc_yAxis(type= (var_scale),
         tickInterval= 1,
         gridLineWidth= 1,
         minorTickInterval= 0.1,
         title = list(text=paste0(Variab)),
         labels=list(format= "{value:,.0f}"),
         opposite=FALSE) %>%
hc_tooltip(shared = FALSE,
             crosshairs=TRUE,
             bacgroundColor="transparent") %>%
hc_credits(enabled = TRUE, text = "Dr. Eric Cabrera Estupinan",
            href = "http://www.htmlwidgets.org/") %>%
   hc_exporting(enabled = TRUE,
             filename="Top_ten_variables_TS",
             formAttribute=list(target="_black"),
             buttons=list(contextButton=list(text="Export",
                                             theme=list(fill="transparent")))) %>%  # enable export
hc_rangeSelector(selected = 4) %>%
hc_navigator( #outlineColor = "gray",
              outlineWidth = 2,
              series = list(color = "red",
                            lineWidth = 2,
                            type = "areaspline", # you can change the type
                            fillColor = "rgba(255, 0, 0, 0.2)"))#,
})  
  
```


All countries map {data-icon="fa-map-o" data-orientation=columns data-navmenu="Countries"}
==========================================================================================

Column {.sidebar}
------------------------------------------------------------------
```{r select-input2}

dateInput(inputId = 'si_2', 
          label = ' Select date', 
          value = max_date,
          min = min_date, 
          max = max_date,
          format="yyyy-mm-dd")
```

```{r select-input9}

 selectInput(inputId = 'si_count4', label = 'Select variable',
             choices = c("Total Confirmed Cases", "Total Confirmed Deaths", "Total Confirmed Recovered",
                         "Case Fatality Rate CFR","Case Recovered Rate CRR", "Cases per 100000 inhab",
                         "Deaths per 100000 inhab", "Recovered per 100000 inhab"), 
             selected = "Total Confirmed Cases", multiple = FALSE)
```

```{r select-input12}

 selectInput(inputId = 'si_count7', label = 'Select Colour Palette',
             choices = c("Viridis", "Reds", "Blues", "Greens"), 
             selected = "Viridis", multiple = FALSE)
```

```{r select-input13}

 selectInput(inputId = 'si_count8', label = 'Select Map Type',
             choices = c("Bubble", "Choropleth"), 
             selected = "Choropleth", multiple = FALSE)
```

```{r slider-input1}

 sliderInput(inputId = 'sli_1', label = 'Resize the bubble',
             min=30, max=50, value=30)
```

Column
------------------------------------------------------------------

### **Countries map** 

```{r}

renderLeaflet({

World_count2=World_count

Map_type<-input$si_count8
#Map_type<-("Choropleth")

var_graph<-input$si_count4
#var_graph<-c("Total Confirmed Cases")

region_map_date<-input$si_2
#region_map_date<-curr_date

Var_col_palette1<-input$si_count7
#Var_col_palette1<-("viridis")

Bubble_size<-input$sli_1
#Bubble_size<-30

if (Var_col_palette1=="Viridis"){
  Var_col_palette1<-c("viridis")
}

if (var_graph=="Total Confirmed Cases"){
  World_count2$count_tot_cases<-as.numeric(NA)
}
if (var_graph=="Total Confirmed Deaths"){
  World_count2$count_tot_deaths<-as.numeric(NA)
}
if (var_graph=="Total Confirmed Recovered"){
  World_count2$count_tot_recovered<-as.numeric(NA)
}
if (var_graph=="Case Fatality Rate CFR"){
  World_count2$CFR<-as.numeric(NA)
}
if (var_graph=="Case Recovered Rate CRR"){
  World_count2$CRR<-as.numeric(NA)
}
if (var_graph=="Cases per 100000 inhab"){
  World_count2$factor1<-as.numeric(NA)
}
if (var_graph=="Deaths per 100000 inhab"){
  World_count2$factor2<-as.numeric(NA)
}
if (var_graph=="Recovered per 100000 inhab"){
  World_count2$factor3<-as.numeric(NA)
}

data_count_map_date<- data1 %>%
  filter(date==region_map_date) %>%
  select(country, total_cases, total_deaths, total_recovered, CFR, CRR,
         factor1, factor2, factor3)

 for (i in 1:nrow(data_count_map_date)){

   count_name=as.character(data_count_map_date[i, 1])
    if (count_name != "Bonaire, Sint Eustatius and Saba"
     & count_name != "Channel Islands"
     & count_name != "Guadeloupe"
     & count_name != "French Guiana"
     & count_name != "Martinique"
     & count_name != "Mayotte"
     & count_name != "West Bank and Gaza"
     & count_name != "Reunion"){

   if (var_graph=="Total Confirmed Cases"){
   World_count2[which(World_count2$country==count_name), 7]=data_count_map_date[i,2]
   }
   if (var_graph=="Total Confirmed Deaths"){
   World_count2[which(World_count2$country==count_name), 7]=data_count_map_date[i,3]
   }
   if (var_graph=="Total Confirmed Recovered"){
   World_count2[which(World_count2$country==count_name), 7]=data_count_map_date[i,4]
   }
   if (var_graph=="Case Fatality Rate CFR"){
   World_count2[which(World_count2$country==count_name), 7]=round(data_count_map_date[i,5], digits = 2)
   }
   if (var_graph=="Case Recovered Rate CRR"){
   World_count2[which(World_count2$country==count_name), 7]=round(data_count_map_date[i,6], digits = 2)
   }
   if (var_graph=="Cases per 100000 inhab"){
   World_count2[which(World_count2$country==count_name), 7]=round(data_count_map_date[i,7], digits = 2)
   }
   if (var_graph=="Deaths per 100000 inhab"){
   World_count2[which(World_count2$country==count_name), 7]=round(data_count_map_date[i,8], digits = 2)
   }
   if (var_graph=="Recovered per 100000 inhab"){
   World_count2[which(World_count2$country==count_name), 7]=round(data_count_map_date[i,9], digits = 2)
   }

 } else {}
 }

if (var_graph=="Total Confirmed Cases"){
  palnumeric <- colorBin(Var_col_palette1, domain = World_count2$count_tot_cases, bins=10, pretty=TRUE, alpha = F, reverse = F)
  popup <- paste0("<b>", "Country: ", "</b>", as.character(World_count2$country),
    "<br>", "<b>", "Confirmed Cases: ", "</b>", World_count2$count_tot_cases)
  col_obj<-World_count2$count_tot_cases
}
if (var_graph=="Total Confirmed Deaths"){
  palnumeric <- colorBin(Var_col_palette1, domain = World_count2$count_tot_deaths, bins=10, pretty=TRUE, alpha = F, reverse = F)
  popup <- paste0("<b>", "Country: ", "</b>", as.character(World_count2$country),
    "<br>", "<b>", "Confirmed Deaths: ", "</b>", World_count2$count_tot_deaths)
  col_obj<-World_count2$count_tot_deaths
}
if (var_graph=="Total Confirmed Recovered"){
  palnumeric <- colorBin(Var_col_palette1, domain = World_count2$count_tot_recovered, bins=10, pretty=TRUE, alpha = F, reverse = F)
  popup <- paste0("<b>", "Country: ", "</b>", as.character(World_count2$country),
    "<br>", "<b>", "Confirmed Recovered: ", "</b>", World_count2$count_tot_recovered)
  col_obj<-World_count2$count_tot_recovered
}
if (var_graph=="Case Fatality Rate CFR"){
  palnumeric <- colorBin(Var_col_palette1, domain = World_count2$CFR, bins=10, pretty=TRUE, alpha = F, reverse = F)
  popup <- paste0("<b>", "Country: ", "</b>", as.character(World_count2$country),
    "<br>", "<b>", "CFR: ", "</b>", World_count2$CFR)
  col_obj<-World_count2$CFR
}
if (var_graph=="Case Recovered Rate CRR"){
  palnumeric <- colorBin(Var_col_palette1, domain = World_count2$CRR, bins=10, pretty=TRUE, alpha = F, reverse = F)
  popup <- paste0("<b>", "Country: ", "</b>", as.character(World_count2$country),
    "<br>", "<b>", "CRR: ", "</b>", World_count2$CRR)
  col_obj<-World_count2$CRR
}
if (var_graph=="Cases per 100000 inhab"){
  palnumeric <- colorBin(Var_col_palette1, domain = World_count2$factor1, bins=10, pretty=TRUE, alpha = F, reverse = F)
  popup <- paste0("<b>", "Country: ", "</b>", as.character(World_count2$country),
    "<br>", "<b>", "Cases per 100000 inhab: ", "</b>", World_count2$factor1)
  col_obj<-World_count2$factor1
}
if (var_graph=="Deaths per 100000 inhab"){
  palnumeric <- colorBin(Var_col_palette1, domain = World_count2$factor2, bins=10, pretty=TRUE, alpha = F, reverse = F)
  popup <- paste0("<b>", "Country: ", "</b>", as.character(World_count2$country),
    "<br>", "<b>", "Deaths per 100000 inhab: ", "</b>", World_count2$factor2)
  col_obj<-World_count2$factor2
}
if (var_graph=="Recovered per 100000 inhab"){
  palnumeric <- colorBin(Var_col_palette1, domain = World_count2$factor3, bins=10, pretty=TRUE, alpha = F, reverse = F)
  popup <- paste0("<b>", "Country: ", "</b>", as.character(World_count2$country),
    "<br>", "<b>", "Recovered per 100000 inhab: ", "</b>", World_count2$factor3)
  col_obj<-World_count2$factor3
}

auxmat<-as.data.frame(col_obj)
auxmat$zoom<-as.numeric(NA)
maxim<-max(auxmat$col_obj)
minim<-min(auxmat$col_obj)
for (i in 1:nrow(auxmat)){
   auxmat[i,2]=Bubble_size-(((maxim-auxmat[i,1])/(maxim-minim))*(Bubble_size-0))
}

if (Map_type=="Bubble"){
    maxim<-max(World_count2$col_obj)
    minim<-min(World_count2$col_obj)
 for (i in 1:nrow(row_data2)){

   count_name=as.character(row_data2[i, 2])
    if (count_name != "Bonaire, Sint Eustatius and Saba"
     & count_name != "Channel Islands"
     & count_name != "Guadeloupe"
     & count_name != "French Guiana"
     & count_name != "Martinique"
     & count_name != "Mayotte"
     & count_name != "West Bank and Gaza"
     & count_name != "Reunion"){
   World_count2[which(World_count2$country==count_name), 3]=row_data2[i,9]
   World_count2[which(World_count2$country==count_name), 4]=row_data2[i,10]
 } else {}
 }
}

World_count2$zoom<-auxmat$zoom
#col_obj<-as.data.frame(col_obj)
World_count2<-cbind(World_count2,col_obj)

#Map generation
if (Map_type=="Choropleth"){

leaflet(options = leafletOptions(dragging=TRUE,
                                 minZoom = 2.2,
                                 maxZoom = 18,
                                 preferCanvas = TRUE)) %>%
  addTiles(group = "OSM (default)") %>%
  addProviderTiles("CartoDB", group="CartoDB",
                   options = providerTileOptions(updateWhenZooming=FALSE,
                                                 updateWhenIdle = TRUE)) %>%
  setView(lng = 0, lat=40, zoom= 2.2) %>%
  addPolygons(data=World_count2,
              color = "#444444" ,
              weight = 1,
              smoothFactor = 0.5,
              opacity = 1.0,
              fillOpacity = 0.5,
              fillColor = ~palnumeric(World_count2$col_obj),    # Color de llenado
              group = (var_graph),
              highlightOptions = highlightOptions(color = "white", weight = 2,
                                                  bringToFront = TRUE), #highlight cuando pasas el cursor
              label = ~World_count2$country,                                  # etiqueta cuando pasas el cursor
              labelOptions = labelOptions(direction = "auto"),
              popup = popup) %>%        # mostrar el popup
          addLegend(position = "bottomleft", pal = palnumeric, values = World_count2$col_obj,
                    group = (var_graph), title= (var_graph), opacity = 1) %>%
  addGraticule(interval = 20, style = list(color = "gray", weight = 1), group="Graticule") %>%
  addLayersControl(baseGroups = c("OSM (default)", "CartoDB"),
    overlayGroups=c("Graticule"),
    options = layersControlOptions(collapsed = TRUE)) %>%
  addMiniMap(tiles = providers$Esri.WorldStreetMap,
    toggleDisplay = TRUE)%>%
    addScaleBar(position = "bottomright", options = scaleBarOptions(maxWidth = 100,
                                                                    metric = TRUE,
                                                                    updateWhenIdle = TRUE)) %>%
    addMeasure(position="bottomleft",
               primaryLengthUnit = "meters",
               primaryAreaUnit = "sqmeters",
               activeColor = "#3D535D",
               completedColor = "#7D4479",
               localization=de)
}else{

  leaflet(options = leafletOptions(dragging=TRUE,
                                 minZoom = 2.2,
                                 maxZoom = 18,
                                 preferCanvas = TRUE)) %>%
  addTiles(group = "OSM (default)") %>%
  addProviderTiles("CartoDB", group="CartoDB",
                   options = providerTileOptions(updateWhenZooming=FALSE,
                                                 updateWhenIdle = TRUE)) %>%
  setView(lng = 0, lat=40, zoom= 2.2) %>%

  addCircleMarkers(data=World_count2, lng = ~Long, lat= ~Lat,
                   radius = ~zoom,
                   color = "red", #~palnumeric(World_count2$col_obj),
                   weight = 1,
                   opacity = 1.0,
                   fillOpacity = 0.5,
                   group = (var_graph),
                   label = ~World_count2$country,
                   labelOptions = labelOptions(direction = "auto"),
                   popup = popup) %>%   # mostrar el popup
#             addLegend(position = "bottomleft", pal = palnumeric, values = World_count2$col_obj,
#                    title= (var_graph), opacity = 1) %>%
      addGraticule(interval = 20, style = list(color = "gray", weight = 1), group="Graticule") %>%
  addLayersControl(baseGroups = c("OSM (default)", "CartoDB"),
    overlayGroups=c("Graticule"),
    options = layersControlOptions(collapsed = TRUE)) %>%
  addMiniMap(tiles = providers$Esri.WorldStreetMap,
    toggleDisplay = TRUE) %>%
    addScaleBar(position = "bottomright", options = scaleBarOptions(maxWidth = 100,
                                                                    metric = TRUE,
                                                                    updateWhenIdle = TRUE))
}
})

```

Forecasting {data-icon="fa-cogs" data-orientation=columns data-navmenu="Models"}
===================================================================================

Column {.sidebar}
------------------------------------------------------------------
```{r select-input23}

dateInput(inputId = 'si_4',
          label = ' Select date',
          value = max_date,
          min = min_date,
          max = max_date,
          format="yyyy-mm-dd")
```

```{r select-input21}

count_list_main<-data1 %>%
  select(country) %>%
  distinct(country)

 count_list_main<-as.character(count_list_main$country)

 selectInput(
   inputId = 'si_count_main1', label = ' Select a Country',
   choices = count_list_main, selected = "US")
```

```{r select-input22}

 selectInput(inputId = 'si_count13', label = 'Select cummulative variable',
             choices = c("Total Confirmed Cases", "Total Confirmed Deaths", "Total Confirmed Recovered"),
             selected = "Total Confirmed Cases", multiple = FALSE)
```

```{r slider-input2}

 sliderInput(inputId = 'sli_2', label = 'Number of day for prediction',
             min=1, max=100, value=28)
```

Column {data-width=600}
------------------------------------------------------------------

### **Forecast variable TS** 

```{r}
 
renderHighchart({

Fcast_date<-input$si_4
#Fcast_date<-as.Date("2020-09-01")

Variab_obj<-input$si_count13
#Variab_obj<-"Total Confirmed Cases"

country_main_sel<-input$si_count_main1
#country_main_sel<-c("US")

Numb_days<-input$sli_2
#Numb_days=28

 if (Variab_obj=="Total Confirmed Cases"){
   Obj_col2<-data1$total_cases
 }
 if (Variab_obj=="Total Confirmed Deaths"){
   Obj_col2<-data1$total_deaths
 }
 if (Variab_obj=="Total Confirmed Recovered"){
   Obj_col2<-data1$total_recovered
 }
 #auxmat<-as.data.frame(col_obj)
 data1a<-cbind(data1,Obj_col2)

 curr_date1<-as.Date(curr_date)

 if (Fcast_date==curr_date1){

 df_calc<-data1a %>%
   filter(country==country_main_sel) %>%
   select(country, date, Obj_col2)

 df_calc_forecast<-data.frame(df_calc$date, df_calc$Obj_col2)
 colnames(df_calc_forecast)<-c("ds","y")

 #Forecasting
 m<-prophet(df_calc_forecast)

 #Prediction
 future<-make_future_dataframe(m, periods = Numb_days)
 forecast<-predict(m, future)

 data_forecats<-forecast[c('ds','yhat','yhat_lower','yhat_upper')]
 colnames(data_forecats)<-c("date","y", "ymin", "ymax")

 data_forecats$y=round(data_forecats$y, digits = 0)
 data_forecats$ymin=round(data_forecats$ymin, digits = 0)
 data_forecats$ymax=round(data_forecats$ymax, digits = 0)
 data_forecats$date<-as.Date(data_forecats$date)

 df_calc$Obj_col2=round(df_calc$Obj_col2, digits = 0)

 highchart (type="stock") %>%
 hc_add_series(data=df_calc,
               name="Real",
               type="scatter",
               color='gray',
               size=1,
               hcaes(x=date, y=Obj_col2)) %>%
 hc_add_series(data=data_forecats,
               name="Forecast Range",
               type="arearange",
               color='#87CEFA',
               fillOpacity=0.3,
               hcaes(x=date, low=ymin, high=ymax)) %>%
 hc_add_series(data=data_forecats,
               name="Forecast Main",
               type="line",
               color='orange',
               hcaes(x=date, y=y)) %>%
   hc_title(text=paste(Variab_obj,"in",country_main_sel,"and forecast for:",Numb_days," days (Time Serie, TS)"),
         align="left",
         useHTML=TRUE) %>%
hc_subtitle(text="<i>Data source: https://github.com/CSSEGISandData/COVID-19/tree/master/csse_covid_19_data/csse_covid_19_time_series",
            align="left",
            useHTML=TRUE) %>%
hc_xAxis(title = list(text="time (days)"),
           type="datetime") %>%
   hc_yAxis(tickInterval= 1,
            gridLineWidth= 1,
            minorTickInterval= 0.1,
            title = list(text=paste0(Variab_obj, " with forecast")),
            labels=list(format= "{value:,.0f}"),
            opposite=FALSE) %>%
hc_legend(enabled = TRUE) %>%
    hc_exporting(enabled = TRUE,
             filename="Forecast_variables_TS",
             formAttribute=list(target="_black"),
             buttons=list(contextButton=list(text="Export",
                                             theme=list(fill="transparent")))) %>%  # enable export
   hc_tooltip(shared = FALSE,
             crosshairs=TRUE,
             bacgroundColor="transparent") %>%
hc_credits(enabled = TRUE, text = "Dr. Eric Cabrera Estupinan",
            href = "http://www.htmlwidgets.org/") %>%
hc_rangeSelector(selected = 4) %>%
hc_navigator( #outlineColor = "gray",
              outlineWidth = 2,
              series = list(color = "red",
                            lineWidth = 2,
                            type = "areaspline", # you can change the type
                            fillColor = "rgba(255, 0, 0, 0.2)"))#,
 }else{

vect_min_date1<-data1a %>%
  filter(country==country_main_sel) %>%
  select(date)

date_min<-as.Date(min(vect_min_date1$date))

df_calc<-data1a %>%
   filter(country==country_main_sel) %>%
  filter(between(date,date_min, Fcast_date)) %>%
   select(country, date, Obj_col2)

df_calc2<-data1a %>%
   filter(country==country_main_sel) %>%
  filter(between(date,Fcast_date, curr_date1)) %>%
   select(country, date, Obj_col2)


 df_calc_forecast<-data.frame(df_calc$date, df_calc$Obj_col2)
 colnames(df_calc_forecast)<-c("ds","y")

 #Forecasting
 m<-prophet(df_calc_forecast)

  #Prediction
 future<-make_future_dataframe(m, periods = Numb_days)
 forecast<-predict(m, future)

 data_forecats<-forecast[c('ds','yhat','yhat_lower','yhat_upper')]
 colnames(data_forecats)<-c("date","y", "ymin", "ymax")

 data_forecats$y=round(data_forecats$y, digits = 2)
 data_forecats$ymin=round(data_forecats$ymin, digits = 2)
 data_forecats$ymax=round(data_forecats$ymax, digits = 2)
 data_forecats$date<-as.Date(data_forecats$date)

 df_calc$Obj_col2=round(df_calc$Obj_col2, digits = 0)
 df_calc2$Obj_col2=round(df_calc2$Obj_col2, digits = 0)
 
 highchart (type="stock") %>%
 hc_add_series(data=df_calc,
               name="Real",
               type="scatter",
               color='gray',
               size=1,
               hcaes(x=date, y=Obj_col2)) %>%
 hc_add_series(data=df_calc2,
               name="Real after selected date",
               type="scatter",
               color='black',
               size=1,
               hcaes(x=date, y=Obj_col2)) %>%
 hc_add_series(data=data_forecats,
               name="Forecast Range",
               type="arearange",
               color='#87CEFA',
               fillOpacity=0.3,
               hcaes(x=date, low=ymin, high=ymax)) %>%
   hc_add_series(data=data_forecats,
               name="Forecast Main",
               type="line",
               color='orange',
               hcaes(x=date, y=y)) %>%
   hc_title(text=paste(Variab_obj, "in",country_main_sel,"and forecast for:",Numb_days," days (Time Serie, TS)"),
         align="left",
         useHTML=TRUE) %>%
hc_subtitle(text="<i>Data source: https://github.com/CSSEGISandData/COVID-19/tree/master/csse_covid_19_data/csse_covid_19_time_series",
            align="left",
            useHTML=TRUE) %>%
hc_xAxis(title = list(text="time (days)"),
           type="datetime") %>%
   hc_yAxis(tickInterval= 1,
            gridLineWidth= 1,
            minorTickInterval= 0.1,
            title = list(text=paste0(Variab_obj," with forecast")),
            labels=list(format= "{value:,.0f}"),
            opposite=FALSE) %>%
hc_legend(enabled = TRUE) %>%
    hc_exporting(enabled = TRUE,
             filename="Forecast_variables_TS",
             formAttribute=list(target="_black"),
             buttons=list(contextButton=list(text="Export",
                                             theme=list(fill="transparent")))) %>%  # enable export
   hc_tooltip(shared = FALSE,
             crosshairs=TRUE,
             bacgroundColor="transparent") %>%
   hc_exporting(enabled = TRUE) %>%  # enable export
hc_credits(enabled = TRUE, text = "Dr. Eric Cabrera Estupinan",
            href = "http://www.htmlwidgets.org/") %>%
hc_rangeSelector(selected = 4) %>%
hc_navigator( #outlineColor = "gray",
              outlineWidth = 2,
              series = list(color = "red",
                            lineWidth = 2,
                            type = "areaspline", # you can change the type
                            fillColor = "rgba(255, 0, 0, 0.2)"))#,
 }
})

```


Column {data-width=400}
------------------------------------------------------------------

### **Variable per weekdays** 

```{r}

renderHighchart({

Fcast_date_a<-input$si_4
#Fcast_date_a<-as.Date("2020-09-01")

Variab_obj_a<-input$si_count13
#Variab_obj_a<-"Total Confirmed Cases"

country_main_sel_a<-input$si_count_main1
#country_main_sel_a<-c("US")

 if (Variab_obj_a=="Total Confirmed Cases"){
   Obj_col2_a<-data1$new_cases
   text_var<-c("New daily cases")
 }
 if (Variab_obj_a=="Total Confirmed Deaths"){
   Obj_col2_a<-data1$new_deaths
   text_var<-c("New daily deaths")
 }
 if (Variab_obj_a=="Total Confirmed Recovered"){
   Obj_col2_a<-data1$new_recovered
   text_var<-c("New daily recovered")
 }
 #auxmat<-as.data.frame(col_obj)
 data1b<-cbind(data1,Obj_col2_a)

 df_calc_a<-data1b %>%
   filter(country==country_main_sel_a) %>%
   select(country, date, Obj_col2_a)
 
 df_calc_a$day <- weekdays(as.Date(df_calc_a$date))
 
  df_calc_a$day_eng<- if_else(df_calc_a$day=="domingo", "Sunday", 
                             if_else(df_calc_a$day=="lunes", "Monday",
                                     if_else(df_calc_a$day=="martes", "Tuesday",
                                             if_else(df_calc_a$day=="mircoles", "Wednesday",
                                                     if_else(df_calc_a$day=="jueves", "Thursday",
                                                             if_else(df_calc_a$day=="viernes", "Friday","Saturday"))))))
 
 
   df_calc_days<-df_calc_a %>% 
   group_by(day_eng) %>% 
   summarise(Suma=sum(Obj_col2_a), prom=mean(Obj_col2_a), n=n())
 
   df_calc_days$prom=round(df_calc_days$prom, digits = 2)
   
   df_calc_days$day_eng <- factor(df_calc_days$day_eng, levels = c("Sunday", "Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday"))
   df_calc_days[order(df_calc_days$day_eng)[1:7], ]

   df_calc_days$prom<-round(df_calc_days$prom, 0)
    
 hchart(df_calc_days, 
       type = "column", 
       hcaes(x=day_eng, y=prom),
       name="Mean by weekdays",
       showInLegend = TRUE) %>% 
hc_colors(getOption("highcharter.color_palette")) %>% 
hc_yAxis(tickInterval= 1,
            gridLineWidth= 1,
            minorTickInterval= 0.2,
            title = list(text=paste0(text_var)),
            labels=list(format= "{value:,.0f}"),
            opposite=FALSE) %>%
hc_xAxis(title = list(text="Days of the week"),
         categories = c("Sunday", "Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday")) %>%
hc_title(text= paste(text_var, "in",country_main_sel_a,"by days of the Week, mean values per days."), 
           align="left",
           useHTML=TRUE) %>% 
 hc_subtitle(text="<i>Data source: https://github.com/CSSEGISandData/COVID-19/tree/master/csse_covid_19_data/csse_covid_19_time_series", 
           align="left",
           useHTML=TRUE) %>%
 hc_legend(enabled = TRUE) %>% 
     hc_exporting(enabled = TRUE,
             filename="Variables_per_weekdays") %>%  # enable export
hc_credits(enabled = TRUE, text = "Dr. Eric Cabrera Estupinan",
           href = "http://www.htmlwidgets.org/") 
})

```

### **Model performance** 

```{r}

renderHighchart({

Fcast_date<-input$si_4
#Fcast_date<-as.Date("2020-09-01")
#Fcast_date<-as.Date(curr_date)

Variab_obj<-input$si_count13
#Variab_obj<-"Total Confirmed Cases"

country_main_sel<-input$si_count_main1
#country_main_sel<-c("US")

Numb_days<-input$sli_2
#Numb_days=28

 if (Variab_obj=="Total Confirmed Cases"){
   Obj_col2<-data1$total_cases
 }
 if (Variab_obj=="Total Confirmed Deaths"){
   Obj_col2<-data1$total_deaths
 }
 if (Variab_obj=="Total Confirmed Recovered"){
   Obj_col2<-data1$total_recovered
 }
 #auxmat<-as.data.frame(col_obj)
 data1a<-cbind(data1,Obj_col2)

 curr_date1<-as.Date(curr_date)

 if (Fcast_date==curr_date1){

 df_calc<-data1a %>%
   filter(country==country_main_sel) %>%
   select(country, date, Obj_col2)

 df_calc_forecast<-data.frame(df_calc$date, df_calc$Obj_col2)
 colnames(df_calc_forecast)<-c("ds","y")

 num_fil<-nrow(df_calc_forecast)

 #Forecasting
 m<-prophet(df_calc_forecast)

 #Prediction
 future<-make_future_dataframe(m, periods = Numb_days)
 forecast<-predict(m, future)

 data_forecast<-forecast[c('ds','yhat','yhat_lower','yhat_upper')]
 colnames(data_forecast)<-c("date","y", "ymin", "ymax")

 data_forecast$y=round(data_forecast$y, digits = 0)
 
 #Model Performance
 pred<-as.data.frame(data_forecast$y[1:num_fil])
 colnames(pred)<-c("pred")
 actual<-as.data.frame(m$history$y)
 colnames(actual)<-c("actual")

 pred_act<-cbind(pred, actual)

 lm.model<- augment(lm(pred~actual, data=pred_act))
 lm.model$.fitted<-round(lm.model$.fitted, digits = 0)

 highchart () %>%
 hc_add_series(data=pred_act,
               name="Predict_vs_Actual",
               type="scatter",
               color='gray',
               hcaes(x=actual, y=pred)) %>%
 hc_add_series(data=lm.model,
                name="lm regression",
                type="line",
                color='red',
                hcaes(x=actual, y=.fitted)) %>%
   hc_title(text=paste(Variab_obj, "forecast Model Performance in",country_main_sel),
         align="left",
         useHTML=TRUE) %>%
hc_subtitle(text="<i>Data source: https://github.com/CSSEGISandData/COVID-19/tree/master/csse_covid_19_data/csse_covid_19_time_series",
            align="left",
            useHTML=TRUE) %>%
hc_xAxis(tickInterval= 1,
            gridLineWidth= 1,
            minorTickInterval= 0.1,
            title = list(text=paste0(Variab_obj," Actual")),
            labels=list(format= "{value:,.0f}"),
            opposite=FALSE) %>%
   hc_yAxis(tickInterval= 1,
            gridLineWidth= 1,
            minorTickInterval= 0.1,
            title = list(text=paste0(Variab_obj," Predicted")),
            labels=list(format= "{value:,.0f}"),
            opposite=FALSE) %>%
hc_legend(enabled = TRUE) %>%
        hc_exporting(enabled = TRUE,
             filename="Model_performance") %>%  # enable export
   hc_tooltip(shared = FALSE,
             crosshairs=TRUE,
             bacgroundColor="transparent") %>%
hc_credits(enabled = TRUE, text = "Dr. Eric Cabrera Estupinan",
            href = "http://www.htmlwidgets.org/")

 }else{

  vect_min_date1<-data1a %>%
  filter(country==country_main_sel) %>%
  select(date)

date_min<-as.Date(min(vect_min_date1$date))

df_calc<-data1a %>%
   filter(country==country_main_sel) %>%
  filter(between(date,date_min, Fcast_date)) %>%
   select(country, date, Obj_col2)

df_calc2<-data1a %>%
   filter(country==country_main_sel) %>%
  filter(between(date,Fcast_date, curr_date1)) %>%
   select(country, date, Obj_col2)

df_calc3<-data1a %>%
   filter(country==country_main_sel) %>%
  filter(between(date,date_min, curr_date1)) %>%
   select(country, date, Obj_col2)

 df_calc_forecast<-data.frame(df_calc$date, df_calc$Obj_col2)
 colnames(df_calc_forecast)<-c("ds","y")

  num_fil<-nrow(df_calc_forecast)
  num_fil2<-nrow(df_calc2)-1

#Forecasting
 m<-prophet(df_calc_forecast)

  #Prediction
 future<-make_future_dataframe(m, periods = Numb_days)
 forecast<-predict(m, future)

 data_forecast<-forecast[c('ds','yhat','yhat_lower','yhat_upper')]
 colnames(data_forecast)<-c("date","y", "ymin", "ymax")

 data_forecast$y=round(data_forecast$y, digits = 0)

 #Model Performance
 pred<-as.data.frame(data_forecast$y[1:(num_fil+num_fil2)])
 colnames(pred)<-c("pred")
 #actual<-as.data.frame(m$history$y[1:(num_fil+num_fil2)])
 actual<-as.data.frame(df_calc3$Obj_col2)
 colnames(actual)<-c("actual")

 pred_act<-cbind(pred, actual)

 lm.model<- augment(lm(pred~actual, data=pred_act))
 lm.model$.fitted<-round(lm.model$.fitted, digits = 0)

  highchart () %>%
 hc_add_series(data=pred_act,
               name="Predict_vs_Actual",
               type="scatter",
               color='gray',
               hcaes(x=actual, y=pred)) %>%
 hc_add_series(data=lm.model,
                name="lm regression",
                type="line",
                color='red',
                hcaes(x=actual, y=.fitted)) %>%
   hc_title(text=paste(Variab_obj, "forecast Model Performance",country_main_sel),
         align="left",
         useHTML=TRUE) %>%
hc_subtitle(text="<i>Data source: https://github.com/CSSEGISandData/COVID-19/tree/master/csse_covid_19_data/csse_covid_19_time_series",
            align="left",
            useHTML=TRUE) %>%
hc_xAxis(tickInterval= 1,
            gridLineWidth= 1,
            minorTickInterval= 0.1,
            title = list(text=paste0(Variab_obj," Actual")),
            labels=list(format= "{value:,.0f}"),
            opposite=FALSE) %>%
   hc_yAxis(tickInterval= 1,
            gridLineWidth= 1,
            minorTickInterval= 0.1,
            title = list(text=paste0(Variab_obj," Predicted")),
            labels=list(format= "{value:,.0f}"),
            opposite=FALSE) %>%
hc_legend(enabled = TRUE) %>%
        hc_exporting(enabled = TRUE,
             filename="Model_performance") %>%  # enable export
   hc_tooltip(shared = FALSE,
             crosshairs=TRUE,
             bacgroundColor="transparent") %>%
hc_credits(enabled = TRUE, text = "Dr. Eric Cabrera Estupinan",
            href = "http://www.htmlwidgets.org/")
   }
})

```

SIR {data-icon="fa-cogs" data-orientation=columns data-navmenu="Models"}
===================================================================================

Column {.sidebar}
------------------------------------------------------------------
```{r select-input24}

dateInput(inputId = 'si_5',
          label = ' Select date',
          value = max_date,
          min = min_date,
          max = max_date,
          format="yyyy-mm-dd")
```

```{r select-input25}

count_list_main<-data1 %>%
  select(country) %>%
  distinct(country)

 count_list_main<-as.character(count_list_main$country)

 selectInput(
   inputId = 'si_count_main2', label = ' Select a Country',
   choices = count_list_main, selected = "US")
```

```{r slider-input3}

 sliderInput(inputId = 'sli_3', label = 'Parameter (a)',
             min=0, max=3, step= 0.001, value=2.5)
```

```{r slider-input4}

  sliderInput(inputId = 'sli_4', label = 'Parameter (b)',
             min=0, max=3, step=0.001, value=0.2)
```

```{r slider-input5}

  sliderInput(inputId = 'sli_5', label = 'Mx time (days)',
             min=1, max=180, step=1, value=21)
```

```{r radio-buttons}

  radioButtons(inputId = 'Rad_1', label = 'Select the graphic opcion',
            choices=list('With susceptible & Recovered', 'Without susceptible & Recovered'),
            selected='With susceptible & Recovered')
```

Column {data-width=650}
------------------------------------------------------------------

### **SRI Model** 

```{r}

renderHighchart({

sir_date<-input$si_5
#sir_date<-as.Date("2020-10-06")
#sir_date<-as.Date(curr_date)

country_sir_sel<-input$si_count_main2
#country_sir_sel<-c("US")

sir_a<-input$sli_3
#sir_a= 2.46

sir_b<-input$sli_4
#sir_b= 0.2

sir_t<-input$sli_5
#sir_t= 14

Rad_var_1<-input$Rad_1
#Rad_var_1<-c("With susceptible & Recovered")

Pob<- row_data2 %>% 
  filter(country==country_sir_sel) %>% 
  summarise(population)

Cases_Recov_start<-data1 %>% 
  filter(country==country_sir_sel) %>% 
  filter(date==sir_date) %>% 
  summarise(total_cases, total_recovered)

S_start<-Pob$population-Cases_Recov_start$total_cases
I_start<-Cases_Recov_start$total_cases
R_start<-Cases_Recov_start$total_recovered

#Poblacin
N<-Pob$population
#Estado inicial
init<-c(S=S_start, 
        I=I_start,
        R=R_start)
#Parametros del modelo
param<-c(sir_a,
         sir_b)
#Funcin con la ODE
sir<- function(times, init, param) {
  with(as.list(c(init, param)), {
#Ecuaciones diferenciales
    dS<--sir_a*S*I/N
    dI<-sir_a*S*I/N - sir_b*I
    dR<-              sir_b*I
#Resultados de las tasas de cambio
    return(list(c(dS, dI, dR)))
  })
}
#Intervalo de tiempo
  times<-seq(1, sir_t, by=1)
#Resolucion del sistema de ecuaciones con la funcion ODE.
  Sol<-ode(y=init, times=times, func=sir, parms=param)
#Convertir Sol a data.frame
  Sol<-as.data.frame(Sol)


start_date<-ymd(sir_date)
Vect_days<-start_date+days(1:sir_t)

Sol$time<-Vect_days
Sol$S<-round(Sol$S, digits = 0) 
Sol$I<-round(Sol$I, digits = 0) 
Sol$R<-round(Sol$R, digits = 0) 

curr_date_sir<-as.Date(curr_date)

if (sir_date==curr_date_sir){
  
highchart (type="stock") %>%
  hc_add_series(data=Sol,
               name="Susceptible",
               type="spline",
               color='blue',
               hcaes(x=time, y=S)) %>%
  hc_add_series(data=Sol,
               name="Infected",
               type="spline",
               color='red',
               hcaes(x=time, y=I)) %>%
  hc_add_series(data=Sol,
               name="Recovered",
               type="spline",
               color='green',
               hcaes(x=time, y=R)) %>%
  hc_title(text=paste("SRI Model for",country_sir_sel, "by days (Time Serie, TS)"),
         align="left",
         useHTML=TRUE) %>%
hc_subtitle(text="<i>Data source: https://github.com/CSSEGISandData/COVID-19/tree/master/csse_covid_19_data/csse_covid_19_time_series",
            align="left",
            useHTML=TRUE) %>%
hc_xAxis(title = list(text="time (days)"),
           type="datetime") %>%
   hc_yAxis(tickInterval= 1,
            gridLineWidth= 1,
            minorTickInterval= 0.1,
            title = "Susceptible, Infected & Recovered",
            labels=list(format= "{value:,.0f}"),
            opposite=FALSE) %>%
hc_legend(enabled = TRUE) %>%
    hc_exporting(enabled = TRUE,
                 filename="SRI_exit",
                 formAttribute=list(target="_black"),
                 buttons=list(contextButton=list(text="Export",
                                             theme=list(fill="transparent")))) %>%  # enable export
   hc_tooltip(shared = FALSE,
             crosshairs=TRUE,
             bacgroundColor="transparent") %>%
hc_credits(enabled = TRUE, text = "Dr. Eric Cabrera Estupinan",
            href = "http://www.htmlwidgets.org/") %>%
hc_rangeSelector(selected = 4) %>%
hc_navigator( #outlineColor = "gray",
              outlineWidth = 2,
              series = list(color = "red",
                            lineWidth = 2,
                            type = "areaspline", # you can change the type
                            fillColor = "rgba(255, 0, 0, 0.2)"))#,

}else{
 
df_cases<-data1 %>%
   filter(country==country_sir_sel) %>%
  filter(between(date,sir_date, curr_date_sir)) %>%
   select(country, date, total_cases)    
  
  if (Rad_var_1=="With susceptible & Recovered"){
  
highchart (type="stock") %>%
    hc_add_series(data=df_cases,
               name="Real infected",
               type="scatter",
               color='black',
               hcaes(x=date, y=total_cases)) %>%  
  hc_add_series(data=Sol,
               name="Susceptible",
               type="spline",
               color='blue',
               hcaes(x=time, y=S)) %>%
  hc_add_series(data=Sol,
               name="Infected",
               type="spline",
               color='red',
               hcaes(x=time, y=I)) %>%
  hc_add_series(data=Sol,
               name="Recovered",
               type="spline",
               color='green',
               hcaes(x=time, y=R)) %>%
  hc_title(text=paste("SRI Model for",country_sir_sel, "by days (Time Serie, TS)"),
         align="left",
         useHTML=TRUE) %>%
hc_subtitle(text="<i>Data source: https://github.com/CSSEGISandData/COVID-19/tree/master/csse_covid_19_data/csse_covid_19_time_series",
            align="left",
            useHTML=TRUE) %>%
hc_xAxis(title = list(text="time (days)"),
           type="datetime") %>%
   hc_yAxis(tickInterval= 1,
            gridLineWidth= 1,
            minorTickInterval= 0.1,
            title = "Susceptible, Infected & Recovered",
            labels=list(format= "{value:,.0f}"),
            opposite=FALSE) %>%
hc_legend(enabled = TRUE) %>%
    hc_exporting(enabled = TRUE,
                 filename="SRI_exit",
                 formAttribute=list(target="_black"),
                 buttons=list(contextButton=list(text="Export",
                                             theme=list(fill="transparent")))) %>%  # enable export
   hc_tooltip(shared = FALSE,
             crosshairs=TRUE,
             bacgroundColor="transparent") %>%
hc_credits(enabled = TRUE, text = "Dr. Eric Cabrera Estupinan",
            href = "http://www.htmlwidgets.org/") %>%
hc_rangeSelector(selected = 4) %>%
hc_navigator( #outlineColor = "gray",
              outlineWidth = 2,
              series = list(color = "red",
                            lineWidth = 2,
                            type = "areaspline", # you can change the type
                            fillColor = "rgba(255, 0, 0, 0.2)"))#,  
  }else{
    
highchart (type="stock") %>%
    hc_add_series(data=df_cases,
               name="Real infected",
               type="scatter",
               color='black',
               hcaes(x=date, y=total_cases)) %>%
  hc_add_series(data=Sol,
               name="Infected",
               type="spline",
               color='red',
               hcaes(x=time, y=I)) %>%
  hc_title(text=paste("SRI Model for",country_sir_sel, "by days (Time Serie, TS)"),
         align="left",
         useHTML=TRUE) %>%
hc_subtitle(text="<i>Data source: https://github.com/CSSEGISandData/COVID-19/tree/master/csse_covid_19_data/csse_covid_19_time_series",
            align="left",
            useHTML=TRUE) %>%
hc_xAxis(title = list(text="time (days)"),
           type="datetime") %>%
   hc_yAxis(tickInterval= 1,
            gridLineWidth= 1,
            minorTickInterval= 0.1,
            title = "Susceptible, Infected & Recovered",
            labels=list(format= "{value:,.0f}"),
            opposite=FALSE) %>%
hc_legend(enabled = TRUE) %>%
       hc_exporting(enabled = TRUE,
                 filename="SRI_exit",
                 formAttribute=list(target="_black"),
                 buttons=list(contextButton=list(text="Export",
                                             theme=list(fill="transparent")))) %>%  # enable export
   hc_tooltip(shared = FALSE,
             crosshairs=TRUE,
             bacgroundColor="transparent") %>%
hc_credits(enabled = TRUE, text = "Dr. Eric Cabrera Estupinan",
            href = "http://www.htmlwidgets.org/") %>%
hc_rangeSelector(selected = 4) %>%
hc_navigator( #outlineColor = "gray",
              outlineWidth = 2,
              series = list(color = "red",
                            lineWidth = 2,
                            type = "areaspline", # you can change the type
                            fillColor = "rgba(255, 0, 0, 0.2)"))#,      
  }   
}
})

```


Column {data-width=350}
------------------------------------------------------------------

### **SIR Model table** 

```{r}
renderDT({

sir_date<-input$si_4
#sir_date<-as.Date("2020-09-01")
#sir_date<-as.Date(curr_date)

country_sir_sel<-input$si_count_main2
#country_sir_sel<-c("US")

sir_a<-input$sli_3
#sir_a= 2.46

sir_b<-input$sli_4
#sir_b= 0.2

sir_t<-input$sli_5
#sir_t= 14

Pob<- row_data2 %>% 
  filter(country==country_sir_sel) %>% 
  summarise(population)

Cases_Recov_start<-data1 %>% 
  filter(country==country_sir_sel) %>% 
  filter(date==sir_date) %>% 
  summarise(total_cases, total_recovered)

S_start<-Pob$population-Cases_Recov_start$total_cases
I_start<-Cases_Recov_start$total_cases
R_start<-Cases_Recov_start$total_recovered

#Poblacin
N<-Pob$population
#Estado inicial
init<-c(S=S_start, 
        I=I_start,
        R=R_start)
#Parametros del modelo
param<-c(sir_a,
         sir_b)
#Funcin con la ODE
sir<- function(times, init, param) {
  with(as.list(c(init, param)), {
#Ecuaciones diferenciales
    dS<--sir_a*S*I/N
    dI<-sir_a*S*I/N - sir_b*I
    dR<-              sir_b*I
#Resultados de las tasas de cambio
    return(list(c(dS, dI, dR)))
  })
}
#Intervalo de tiempo
  times<-seq(1, sir_t, by=1)
#Resolucion del sistema de ecuaciones con la funcion ODE.
  Sol<-ode(y=init, times=times, func=sir, parms=param)
#Convertir Sol a data.frame
  Sol<-as.data.frame(Sol)

start_date<-ymd(sir_date)
Vect_days<-start_date+days(1:sir_t)

Sol$time<-Vect_days  
Sol$S<-round(Sol$S, digits = 2) 
Sol$I<-round(Sol$I, digits = 2) 
Sol$R<-round(Sol$R, digits = 2) 

datatable(Sol,
          caption = "SIR Model result.",
          rownames = T,
          filter = "top",
          extensions= c('Select','Buttons', 'ColReorder', 'KeyTable', 'Responsive', 'Scroller'),
          options = list(pageLength=25,
                         dom = 'Blfrtip',
                         buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                         lengthMenu=list(c(10, 25, 50, -1), c(10, 25, 50, "All")),
                         colReorder = TRUE),
selection = 'none')
})

```

Tables {data-icon="fa-table" data-orientation=columns data-navmenu="Tables"}
============================================================================
Column {.sidebar}
------------------------------------------------------------------
```{r select-input26}

count_list_main_DT<-data1 %>%
  select(country) %>%
  distinct(country)

 count_list_main_DT<-as.character(count_list_main_DT$country)

 selectInput(
   inputId = 'si_count_DT1', label = ' Select a Country',
   choices = count_list_main_DT, selected = "US")

```

Column {data-width=500}
------------------------------------------------------------------
### **Table 1** 
```{r}

renderDT({  
  
 countries_DT<-input$si_count_DT1
#countries_DT<-c("US") 

data1DT<-data1 %>% 
  filter(country==countries_DT) %>% 
  select(iso_code:new_recovered, region, CFR, CRR)
 
datatable(select(data1DT, iso_code:new_recovered, region, CFR, CRR),
          caption = "Main covid-19 data base.",
          rownames = T,
          filter = "top",
          extensions= c('Select','Buttons', 'ColReorder', 'KeyTable', 'Responsive', 'Scroller'),
          options = list(pageLength=25,
                         dom = 'Blfrtip',
                         buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                         lengthMenu=list(c(10, 25, 50, -1), c(10, 25, 50, "All")),
                         colReorder = TRUE),
selection = 'none')
  
})
```

Column {data-width=500}
------------------------------------------------------------------
### **Table 2** 
```{r}
row_data2_DT<-row_data2

row_data2_DT$country<-factor(row_data2_DT$country)
row_data2_DT$iso_code<-as.factor(row_data2_DT$iso_code)
row_data2_DT$region<-as.factor(row_data2_DT$region)
row_data2_DT$income<-as.factor(row_data2_DT$income)
row_data2_DT$year<-as.factor(row_data2_DT$year)

datatable(row_data2_DT,
          caption = "World general data",
          rownames = T,
          filter = "top",
          extensions= c('Select','Buttons', 'ColReorder', 'KeyTable', 'Responsive', 'Scroller'),
          options = list(pageLength=25,
                         dom = 'Blfrtip',
                         buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                         lengthMenu=list(c(10, 25, 50, -1), c(10, 25, 50, "All")),
                         colReorder = TRUE),
selection = 'none')
```


Help
======================================

### **Information**

Help to understand

* Total confirmed cases: Total de personas confirmadas con la COVID-19, es un valor acumulado (nunca disminuye).

* New confirmed cases: Cantidad de personas confirmadas el dia de actualizacion de los datos.

* Total confirmed deaths: Total de personas confirmadas fallecidas por la COVID-19, es un valor acumulado (nunca disminuye).

* New confirmed deaths: Cantidad de personas confirmadas fallecidas el dia de actualizacion de los datos.

* Total confirmed recovered: Total de personas confirmadas recuperadas de la COVID-19, es un valor acumulado (nunca disminuye).

* New confirmed recovered: Cantidad de personas confirmadas recuperadas el dia de actualizacion de los datos.

* Case Fatality Rate CFR: Letalidad o Porciento de defunciones, CFR (%)= (confirmed deaths/ confirmed cases)* 100

                          0%<= CFR <= 3%  FINE     (color green)    
                          3%<= CFR <= 7%  AVERAGE  (color yelow)      
                          7%<= CFR <= 10% WARNING  (color red)

* Case Recovered Rate CRR: Porciento de recuperados, CRR (%)= (confirmed reovered/ confirmed cases)* 100

                          0%<= CFR <= 30%   WARNING  (color red)    
                         30%<= CFR <= 60%   AVERAGE  (color yelow)      
                         60%<= CFR <= 100%  FINE     (color green)

* TS: Time series, Series temporales.

Main sites visited

* https://github.com/CSSEGISandData/COVID-19/tree/master/csse_covid_19_data/csse_covid_19_time_series

* https://ourworldindata.org/coronavirus-source-data

* https://covid19.who.int/

* https://www.arcgis.com/apps/opsdashboard/index.html#/bda7594740fd40299423467b48e9ecf6

* https://www.coronavirusecuador.com/estadisticas-covid-19/

* https://fict-espol.maps.arcgis.com/apps/opsdashboard/index.html#/0ade486cbd384072aee0be1099a84f5f

* https://public.tableau.com/profile/direcci.n.nacional.de.vigilancia.epidemiol.gica.msp#!/vizhome/COVID19ecu_MSP_DNVE/COVID-19MSP

* https://covid19cubadata.github.io/#cuba


About report
======================================

Created by: Ing. Eric Cabrera Estupinan, PhD

Docente - Investigador: Facultad de Ingeniera. Universidad Laica "Eloy Alfaro" de Manab ULEAM. Manta (Ecuador).

Especialista en Gestin de Recursos Hdricos.

Telfono: +593 99 318 9101

E-mail: ecabrerae@gmail.com / eric.cabrera@uleam.edu.ec